---
title: "2020 to 2023 analysis w/ CR and insurance"
output: html_notebook:
  keep_md: TRUE
---
## Setup
Code to load packages
```{r}
#packages
library(tidyverse)
library(readxl)
library(readr)
library(parsedate)
library(janitor)
library(lubridate)
library(labelled)
library(overviewR)
```

Code to load data
```{r}
library(readxl)
visit_pull <- read_excel("C_F_AllPatients_2020to2023.xlsx", na = c(" ", "", "NA")) %>%  as_tibble()
chart_review <- C_F_AdultChartReview_2020to2022 <- read_excel("C_F_AdultChartReview_2020to2022.xlsx", 
                                                              col_types = c("skip", "skip", "numeric", "date", "numeric", "text", "date","numeric", "numeric", "numeric", "text", "text", "numeric", "text", "text", "text", "numeric", "skip","text", "skip", "text", "text", "text", "text", "numeric", "text", "numeric", "text", "skip", "text", "text", "skip"), na = c("NA", "na", "")) %>% as_tibble()
path <- "C_F_All_Insurance_Pull.xlsx"
insurance <-path |>
  excel_sheets() |>
  set_names() |> map(read_excel, path = path) |> list_rbind() |> as_tibble()
```
visit_pull has 942 obs of 192 variables
chart_review has 691 obs of 36 variables
insurance has 415 obs of 25 variables
cleaning names:
```{r}
#name cleaning
cn_visit_pull <-clean_names(visit_pull)
cn_visit_pull <- cn_visit_pull %>% rename(pat_enc_csn_id = pat_enc_csn_id_1) %>% mutate(pat_enc_csn_id = as.character(pat_enc_csn_id))
cn_chart_review <-clean_names(chart_review)
cn_chart_review <- cn_chart_review %>% mutate(pat_enc_csn_id = as.character(pat_enc_csn_id))
cn_insurance <-clean_names(insurance)
#optional removing of old DF
rm(chart_review,visit_pull,insurance,path)
```
reformatting before join
```{r}
origin <- "1904-01-01"
# set TZ to east coast standard
time_zone <- "America/New_York"
#pathway went live on 7/13/21
pathway_start <- mdy("7/13/21", tz = time_zone)
#Story board notification went live on 9/8/21
sb_start <- mdy("9/8/21", tz = time_zone)
# Date CDC put out new STI tx guidelines
CDC_STI_date <- mdy("7/23/2021", tz = time_zone)
rf_visit_pull <- cn_visit_pull %>% mutate(
  arrive_dt = as_datetime(ed_arrival_time, tz = time_zone),
  ed_arrival_date = as_date(ed_arrival_date),
  wtf_departure_dt = as_datetime(ed_departure_time, tz = time_zone),
  # don't use this one for now. Altered by obs/psych/admit pts?
  dispo_dt = as_datetime(ed_disposition_time, tz = time_zone),
  avs_dt = as_datetime(ed_avs_printed_ts, tz = time_zone),
  pt_seen_dt = as_datetime(seen_by_provider_ts, tz = time_zone),
  ed_depart_dt = as_datetime(ed_depart_ts, tz = time_zone),
  #departure TS seems to be the one that is earlier,  departure_time usually later (affected by obs/admit?)
  patient_birth_date = as_date(patient_birth_date, tz = time_zone)
) %>%
  mutate(exposure.num = case_when(arrive_dt < pathway_start ~ 0,
                                  arrive_dt > sb_start ~ 1,
                                  .default = NA)) %>%
  mutate(between = case_when(arrive_dt >= pathway_start &
                               arrive_dt <= sb_start ~ 1,
                             .default = 0)) %>%
  mutate(
    exposure.char = case_when(
      exposure.num == 0 ~ "pre intervention",
      exposure.num == 1 ~ "post intervention",
      between == 1 ~ "between period",
      .default = NA
    )
  ) %>%
  mutate(
    ed_disposition = factor(ed_disposition, ordered = FALSE),
    exposure.char = factor(
      exposure.char,
      ordered = FALSE,
      levels = c("pre intervention", "between period", "post intervention")
    ),
    pathway = factor(agile_md_used_yn, exclude = NULL),
    patient_birth_date = as_date(patient_birth_date)
  ) %>%
  add_count(mrn) %>%
  rename(num_visits = n) %>%
  dplyr::mutate(
    repeater = case_when(num_visits > 1 ~ TRUE,
                         num_visits == 1 ~ FALSE,
                         .default = FALSE),
    race = factor(patient_race, ordered = FALSE),
    age_group = factor(
      age_group,
      levels = c(
        "0-12 yrs",
        "13-16 yrs",
        "17-19 yrs",
        "20-29 yrs",
        "30-39 yrs",
        "40-49 yrs",
        "50-59 yrs",
        "60-69 yrs",
        "70-79 yrs",
        "80-89 yrs",
        "90-99 yrs"
      ),
      ordered = TRUE
    ),
    minor = case_when(age < 18 ~ 1,
                      age >= 18 ~ 0),
    intervention = factor(exposure.char)
  ) %>%
  dplyr::mutate(
    race_bwo = case_when(
      race == "White" ~ "White",
      race == "Black or African American" ~ "Black",
      race != c("White", "Black or African American") ~ "Other"
    ),
    female = case_when(gender == "Female" ~ 1,
                       gender == "Male" ~ 0),
    age_3_group = case_when(age < 18 ~ "< 18",
                            age >= 18 & age < 55 ~ "18 - 55",
                            age >= 55 ~ "55+")
  ) %>%
  dplyr::mutate(
    female_u55 = ifelse(age < 55 & female == 1, 1, 0),
    white = ifelse(race_bwo == "White", 1, 0),
    black = ifelse(race_bwo == "Black", 1, 0),
    other = ifelse(race_bwo == "Other", 1, 0)
  )

levels(rf_visit_pull$pathway) <-
  list("Didn't Use Pathway" = "N", "Used Pathway" = "Y")
# need to also reformat cn_chart_review ed arrival date to get same format
cn_chart_review <- cn_chart_review %>% 
  mutate(ed_arrival_date = as_date(ed_arrival_date))

```

#Joining datasets, excluding patients
```{r}

minors <- rf_visit_pull %>% filter(age < 18)
adult_visit_pull <- rf_visit_pull %>% filter(age >= 18) %>%  mutate(ed_arrival_date = date(arrive_dt))
#now joining in minors as well with plan to filter them out at the end
DF1 <- left_join(rf_visit_pull, cn_chart_review, by = join_by(pat_enc_csn_id == pat_enc_csn_id, ed_arrival_date == ed_arrival_date, mrn == mrn))
s_insurance <- cn_insurance %>% select(pat_enc_csn_id, age, primary_coverage_payor_name, primary_coverage_benefit_plan_name, ed_arrival_year, ed_arrival_month) %>% mutate(pat_enc_csn_id = as.character(pat_enc_csn_id))

DF2 <- left_join(DF1, s_insurance, by = join_by(age.x == age, ed_arrival_month == ed_arrival_month, pat_enc_csn_id == pat_enc_csn_id)) %>% rename(age = age.x)

npts<- n_distinct(DF2$pat_enc_csn_id, na.rm=TRUE) %>% as.character()
nminors <-n_distinct(minors$pat_enc_csn_id, na.rm=TRUE) %>% as.character()
cat("-DF 2 is now the visit pull data with addended chart review data and additional insurance data. Total patients", npts,".   ")
cat("-", nminors, "minor patients were excluded")

rm(npts, nminors)

```

#Main Dataframe (to be re-uploaded to onedrive)
```{r}
variables1 <- colnames(cn_chart_review)
variables2 <-
  DF2 %>% select(arrive_dt:primary_coverage_benefit_plan_name.y) %>% colnames()
variables3 <-
  DF2 %>% select(ends_with(c(
    "ts", "num", "id", "yn", "name", "dt", "time", "zip", "name"
  ))) %>% colnames()
vars <- c(variables1, variables2, variables3)
#r stands for reduced
r_DF1 <- DF2 %>%
  select(matches(vars)) %>%
  mutate(
    insurance_cov = case_when(
      !is.na(primary_coverage_benefit_plan_name.x) ~ primary_coverage_benefit_plan_name.x,
      is.na(primary_coverage_benefit_plan_name.x) & !is.na(primary_coverage_benefit_plan_name.y) ~ primary_coverage_benefit_plan_name.y,
      .default = NA
    )
  ) %>%
  mutate(
    insurance_pay = case_when(
      !is.na(primary_coverage_payor_name.x) ~ primary_coverage_payor_name.x,
      is.na(primary_coverage_payor_name.x) & !is.na(primary_coverage_payor_name.y) ~ primary_coverage_payor_name.y,
    )
  ) # %>%
  #no longer need: mutate(reason_to_exclude = case_when(is.na(reason_to_exclude) ~ 0, .default = reason_to_exclude))

```

insurance categories:
```{r}
Medicare <-("MCR|MEDICARE|CONNECTICARE")
Medicaid <-("MCD|HUSKY|MEDICAID" )
SA_insurance <-("SEXUAL|ASSAULT")
private<-("UNITED HEALTHCARE|AETNA|HARVARD PILGRIM|BCBS|CENTURY PREFERRED|OXFORD|CIGNA|COMMERCIAL GENERIC|YALE|TRICARE|OSCAR|UNITED HEALTHCARE|STIRLING|MERITAIN")
r_DF2 <- r_DF1 %>% mutate(
  insurance = case_when(
    str_detect(insurance_pay, paste(Medicare)) ~ "Medicare",
    str_detect(insurance_pay, paste(Medicaid)) ~ "Medicaid",
    str_detect(insurance_pay, paste(SA_insurance)) ~ "Sexual Assault",
    str_detect(insurance_pay, paste(private)) ~ "Private Insurance",
    is.na(insurance_pay) ~ "Uninsured/Self-Pay",
    insurance_pay == "0" ~"Uninsured/Self-Pay",
    .default = insurance_pay
  )
)
cat("The insurance categories are:", unique(r_DF2$insurance))
```

## trauma patient data:
need to first re-format so single CSN per row, multiple dx columns doesn't work (too many)
plan: make new variable for dx category, then consolidate by grouping by ICD10 codes, ESI level, Procedure (imaging)
```{r}
library(readr)
C_F_Trauma <- read_csv("C_F_Trauma.csv", 
    col_types = cols(order_time = col_skip(), 
        exam_begin_time = col_skip(), authorizing_provider_type = col_skip(), 
        final_dx_poa_c = col_skip(), dx_poa_flag = col_skip()))

```


### ICD10 dx categories:
```{r}
#import dataset w/ classifiers:
DY_ICD <- read_excel("DY_ICD10_Classifications.xlsx")
ICD_names <- DY_ICD %>% 
  pivot_longer(
    everything(),
    cols_vary = "slowest",
    names_to = "category",
    values_to = "dx",
    values_drop_na = TRUE
  ) %>% 
  relocate(dx, .before = category) %>% 
  mutate(category = if_else(
    category %in% c("Other...12", "Other...13"), "Other", category
  )) %>% 
  distinct()
#creating dx category vectors
etoh <- ICD_names %>% filter(category == "Alcohol") %>% pull(var = dx, name = category)
pain <-  ICD_names %>% filter(category == "Pain") %>% pull(var = dx, name = category)
psych <-  ICD_names %>% filter(category == "Psychiatry") %>% pull(var = dx, name = category)
drugs <-  ICD_names %>% filter(category == "Illicit Drug Use") %>% pull(var = dx, name = category)
minor_injury <- ICD_names %>% filter(category == "Minor Injury") %>% pull(var = dx, name = category)
major_injury <- ICD_names %>% filter(category == "Minor Injury") %>% pull(var = dx, name = category)
sdoh <- ICD_names %>% filter(category == "Homelessness/SDOH") %>% pull(var = dx, name = category)

```
New variable of dx categories for trauma set

```{r}
C_F_Trauma_dxcat <- C_F_Trauma %>% 
  mutate(
    Etoh = if_else(dx_name %in% etoh, 1, NA),
    Pain = if_else(dx_name %in% pain, 1, NA),
    Psych = if_else(dx_name %in% psych, 1, NA),
    Drugs = if_else(dx_name %in% drugs, 1, NA),
    Minor_injury = if_else(dx_name %in% minor_injury, 1, NA),
    Major_injury = if_else(dx_name %in% major_injury, 1, NA),
    SDOH = if_else(dx_name %in% sdoh, 1, NA),
    )

```


Now shorten and condense to prep for join
```{r}
short_trauma <- C_F_Trauma_dxcat %>% 
  select(pat_enc_csn_id, esi_level, trauma_case_yn) %>% distinct() 
```

```{r}
a<- C_F_Trauma_dxcat %>%  select(pat_enc_csn_id, Etoh) %>% filter(!is.na(Etoh)) %>% distinct()
b<- C_F_Trauma_dxcat %>%  select(pat_enc_csn_id, Pain) %>% filter(!is.na(Pain)) %>% distinct()
c<-C_F_Trauma_dxcat %>%  select(pat_enc_csn_id, Psych) %>% filter(!is.na(Psych)) %>% distinct()
d<-C_F_Trauma_dxcat %>%  select(pat_enc_csn_id, Drugs) %>% filter(!is.na(Drugs)) %>% distinct()
e<-C_F_Trauma_dxcat %>%  select(pat_enc_csn_id, Minor_injury) %>% filter(!is.na(Minor_injury)) %>% distinct()
f<-C_F_Trauma_dxcat %>%  select(pat_enc_csn_id, Major_injury) %>% filter(!is.na(Major_injury)) %>% distinct()
g<-C_F_Trauma_dxcat %>%  select(pat_enc_csn_id, SDOH) %>% filter(!is.na(SDOH)) %>% distinct()
```
join them all back

```{r}
short_trauma_cat<-left_join(short_trauma, a, by = join_by(pat_enc_csn_id))
short_trauma_cat<-left_join(short_trauma_cat, b, by = join_by(pat_enc_csn_id))
short_trauma_cat<-left_join(short_trauma_cat, c, by = join_by(pat_enc_csn_id))
short_trauma_cat<-left_join(short_trauma_cat, d, by = join_by(pat_enc_csn_id))
short_trauma_cat<-left_join(short_trauma_cat, e, by = join_by(pat_enc_csn_id))
short_trauma_cat<-left_join(short_trauma_cat, f, by = join_by(pat_enc_csn_id))
short_trauma_cat<-left_join(short_trauma_cat, g, by = join_by(pat_enc_csn_id))
rm(a,b,c,d,e,f,g)
```
## joining trauma/dx/ esi data with other joined DF
```{r}

```



## creating cohorts
```{r}
excluded_patients <- r_DF2 %>% filter(!is.na(exclude))
r_DF3 <- r_DF2 %>% filter(is.na(exclude))
excluded_patients %>% group_by(reason_to_exclude) %>% summarise(n=n())
n_excluded <-n_distinct(excluded_patients$pat_enc_csn_id, na.rm=TRUE) %>% as.character()
cat("-", n_excluded, "patients were excluded based on chart review.")
rm(n_excluded)
```


```{r}
post_WO <- r_DF3 %>% filter(ed_arrival_date > sb_start)
```

# Merge in trauma, dx. 
