---
title: "SA Paper 1 Analysis"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
---


## Prep Code

```{r Initial Data and Package Prep, message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(tidyverse)
library(lubridate)
library(gtsummary)
library(gt)
library(parsedate)
library(janitor)
library(labelled)
library(parameters)
library(survival)
library(ggsurvfit)
library(table1)
library(hms)
all_pts <- read_csv("~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/SA_pts_reformatted.csv")
# set TZ to east coast standard
time_zone <- "America/New_York"
#pathway went live on 7/13/21
pathway_start <- mdy("7/13/21", tz = time_zone)
#Story board notification went live on 9/8/21
sb_start <- mdy("9/8/21", tz = time_zone)
day.arrival.start <- hms::as_hms("03:00:00")
night.arrival.start <- hms::as_hms("15:00:00")
# making outcome variable for if correct STI tx: CTX, azithromycin or doxy (and flagyl if female) are ordered 
all_pts <- all_pts %>% mutate(
  azithro_or_doxy = case_when(
    azithromycin_ordered_num | doxycycline_ordered_num == 1 ~ 1,
    azithromycin_ordered_num == 0 &
      doxycycline_ordered_num == 0 ~ 0,
    .default = 0
  )
) %>% mutate(
  sti_tx = case_when(
    gender == "Male" &
      ceftriaxone_ordered_num == 1 & azithro_or_doxy == 1 ~ 1,
    gender == "Male" &
      ceftriaxone_ordered_num | azithro_or_doxy == 0  ~ 0,
    gender == "Female" &
      ceftriaxone_ordered_num == 1 &
      azithro_or_doxy == 1 &
      flagyl_or_metronidazole_ordered_num == 1 ~ 1,
    gender == "Female" &
      ceftriaxone_ordered_num |
      azithro_or_doxy |
      flagyl_or_metronidazole_ordered_num == 0 ~ 0,
    .default = 0
  ),
  chem_ordered = case_when(
    cmp_ordered_yn == "Y" | bmp_ordered_yn == "Y" ~ 1,
    cmp_ordered_yn == "N" & bmp_ordered_yn == "N" ~ 0,
    .default = NA
  ),
  abx_given = case_when(
    ceftriaxone_ordered_num == 0 &
      azithro_or_doxy == 0 &
      flagyl_or_metronidazole_ordered_num == 0 ~ 0,
    ceftriaxone_ordered_num == 1 |
      azithro_or_doxy == 1 |
      flagyl_or_metronidazole_ordered_num == 1 ~ 1
  ),
  lfts_ordered = case_when(
    cmp_ordered_yn == "Y" | lft_ordered_yn == "Y" ~ 1,
    cmp_ordered_yn == "N" & lft_ordered_yn == "N" ~ 0,
    .default = NA
  )
) %>% mutate(
  hiv_labs = case_when(
    hiv_pep_kit_ordered_num == 1 &
      chem_ordered == 1 & lfts_ordered == 1 ~ 1,
    hiv_pep_kit_ordered_num == 1 &
      (chem_ordered == 0| lfts_ordered == 0) ~ 0,
    .default = 0
  ),
  prevent.preg = case_when(
    plan_b_or_levonorgestrel_ordered_num == 1 | ulipristal_ordered_num == 1 ~ 1,
    plan_b_or_levonorgestrel_ordered_num == 0 & ulipristal_ordered_num == 0 ~ 0,
    .default = NA
  ),
  advocate_offered = case_when(
    patient_advocate_called == 1 | patient_advocate_called == 3 ~ "Advocate Offered",
    patient_advocate_called == 0 | patient_advocate_called == 2 ~ "No Documentation of Pt Advocate",
    .default = NA
  ),
  sane_kit_YN = case_when(
    sane_kit_done == 0 ~ "No",
    sane_kit_done == 1 ~ "Yes",
    sane_kit_done == 2 ~ "Offered, but declined",
    sane_kit_done == 3 ~ "Outside 120 hr Window",
    sane_kit_done == 4 ~ "Not done due to concurrent psychiatric concerns"
  ),
  sane_kit_missed = case_when(
    sane_kit_done == 0 ~ "SANE kit not done/documented",
    sane_kit_done %in% c(1,2,3) ~ "SANE kit done/not indicated",
    sane_kit_done == 4 ~ "Not done due to concurrent psychiatric concerns"
  )
) %>% 
  mutate(
    tbl_sti_tx = case_when(
      sti_tx == 1 & abx_given == 1 ~ 1,
      sti_tx == 0 & abx_given == 1 ~ 0,
      .default = NA
    ),
    tbl_hiv_labs = case_when(
      hiv_pep_kit_ordered_num == 1 & hiv_labs == 1 ~ 1,
       hiv_pep_kit_ordered_num == 1 & hiv_labs == 0 ~ 0,
      .default = NA
    ),
    tbl_preg_test = case_when(
      female_u55 == 1 & pregnancy_test_ordered_num == 1 ~ 1,
      female_u55 == 1 & pregnancy_test_ordered_num == 0 ~ 0,
      .default = NA
    ),
      tbl_prevent_preg = case_when(
      female_u55 == 1 & prevent.preg == 1 ~ 1,
      female_u55 == 1 & prevent.preg == 0 ~ 0,
      .default = NA
      ),
    under120h = case_when(
    time_since_sexual_assault_if_number_k_is_y == 0 |  time_since_sexual_assault_if_number_k_is_y == 1 ~ TRUE,
    time_since_sexual_assault_if_number_k_is_y == 2 |  time_since_sexual_assault_if_number_k_is_y == 3 ~ FALSE,
    .default = NA
  ),
  english = case_when(
    patient_language == "English" ~ 1,
    is.na(patient_language) ~ NA,
    .default = 0
  ),
  ambulance = if_else(method_of_arrival == 1, 1, 0),
  relationship_with_patient = factor(relationship_with_patient, levels = c(0,1,2,3,4,NA), labels = c("Unknown","Aqauintance", "Family member", "Stranger", "Intimate Partner", NA), exclude = NULL, ordered = FALSE ),
  insurance_3 = case_when(
    insurance == "Private Insurance" ~ "Private",
    insurance %in% c("Medicaid", "Medicare", "Sexual Assault") ~ "Public",
    insurance == "Uninsured/Self-Pay" ~ "Uninsured"
  ),
  SA_insurance = if_else(
    insurance == "Sexual Assault", 1, 0
  )
  ) %>% 
    mutate(relationship_4_with_pt = case_when(
    relationship_with_patient == "Family member" ~ "Family",
    relationship_with_patient == "Aqauintance" ~ "Aquaintaince",
    relationship_with_patient == "Intimate Partner" ~ "Intimate Partner",
    relationship_with_patient == "Unknown" |relationship_with_patient == "Stranger" ~ "Stranger/Unknown"
  ),
  ipv = if_else(relationship_with_patient == "Intimate Partner", 1, 0)
  ) %>% 
  mutate(arrive_time = as_hms(arrive_dt)) %>% 
  mutate(day_night = case_when(
    arrive_time >= day.arrival.start & arrive_time <= night.arrival.start ~ "Day",
    arrive_time < day.arrival.start | arrive_time > night.arrival.start ~ "Night",
    .default = "ERROR"
  )) %>% 
  mutate(threeto3 = if_else(day_night == "Day", 1, 0))
all_pts$insurance_3 <- as_factor(all_pts$insurance_3)
all_pts$insurance_3 <- relevel(all_pts$insurance_3, ref = "Public")

between_pts <- all_pts %>% filter(between == 1)
n_between <- n_distinct(between_pts$pat_enc_csn_id, na.rm=TRUE) %>% as.character()
pp.cohort.1 <- all_pts %>% filter(between == 0) %>% filter(age > 17)
excluded_patients <- pp.cohort.1  %>% filter(!is.na(exclude))
pp.cohort.2 <- pp.cohort.1  %>% filter(is.na(exclude))
excluded_patients <- excluded_patients %>% add_value_labels(reason_to_exclude = c( "Seen earlier" = 1 , "Patient reports not being assaulted" = 2, "Psych" = 3, "not excluded" = 4, "Eloped" = 5)) %>% to_factor()
excluded_patients %>% group_by(reason_to_exclude) %>% summarise(n=n())
n_excluded <-n_distinct(excluded_patients$pat_enc_csn_id, na.rm=TRUE) %>% as.character()
cat(" ", n_between, "patients who arrived between 7/13/21 and 9/8/21 were excluded")
cat("-", n_excluded, "patients were excluded based on chart review.")
number_of_minors <-all_pts %>% filter(between == 0) %>% filter(age < 18)
number_of_minors <- n_distinct(number_of_minors$pat_enc_csn_id, na.rm = TRUE) %>% as.character()
cat("  ", number_of_minors, "patients under 18 YO excluded")
rm(n_excluded, number_of_minors, n_between)
cohort.1 <- all_pts %>% filter(ed_arrival_date > sb_start) %>% filter(age > 17) %>% filter(is.na(exclude))
```

942 patient encounters from 2019-12-31 to 2022-12-24  
76 patients who arrived between 7/13/21 and 9/8/21 were excluded  
247 patients under 18 YO excluded  
36 patients were excluded based on chart review (13 seen earlier, 13 reported not actually being assaulted, 2 were purely psychiatric presentations, 8 eloped before evaluation could be completed) 

## Table 1 and 2

```{r echo=FALSE, message=FALSE, warning=FALSE}
pp.cohort.2$exposure.char <- as_factor(pp.cohort.2$exposure.char)
pp.table.1 <- pp.cohort.2 %>%
  arrange((exposure.num)) %>%
  select(
    exposure.char,
    age,
    female,
    race_bwo,
    under120h,
    english,
    ambulance,
    insurance,
    Psych,
    Etoh,
    Drugs,
    relationship_with_patient
  ) %>%
  set_variable_labels(
    age = "Age",
    female = "Female",
    race_bwo = "Race",
    under120h = "Presented within 120 of assault",
    ambulance = "Arrived by EMS",
    english = "English speaking",
    insurance = "Insurance",
    relationship_with_patient = "Relation of assailant to patient"
  ) %>%
  tbl_summary(
    by = exposure.char,
    missing = "ifany",
    percent = "column",
    statistic = (age ~ "{median} ({p25}, {p75})")
  ) %>%
  add_p() %>% separate_p_footnotes()
table.1 <- cohort.1 %>%
  select(
    pathway,
    age,
    female,
    race_bwo,
    under120h,
    english,
    ambulance,
    insurance,
    Psych,
    Etoh,
    Drugs,
    relationship_with_patient
  ) %>%
  set_variable_labels(
    age = "Age",
    female = "Female",
    race_bwo = "Race",
    under120h = "Presented within 120 of assault",
    ambulance = "Arrived by EMS",
    english = "English speaking",
    insurance = "Insurance",
    relationship_with_patient = "Relation of assailant to patient"
  ) %>%
  tbl_summary(
    by = pathway,
    missing = "ifany",
    percent = "column",
    statistic = (age ~ "{median} ({p25}, {p75})")
  ) %>%
  add_p() %>% separate_p_footnotes()
table1 <-
  tbl_merge(
    list(pp.table.1, table.1),
    tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")
  ) %>% as_gt()
table1
```

```{r tables, echo=FALSE, message=FALSE, warning=FALSE}
pp.table.2 <- pp.cohort.2 %>% select(exposure.char, advocate_offered, abx_given, sti_tx, hiv_pep_kit_ordered_num, hiv_labs, female_u55, pregnancy_test_ordered_num, prevent.preg, sane_kit_YN, sane_kit_missed, follow_up_at_discharge) %>% 
 set_variable_labels(advocate_offered = "Documentation of advocate contacted", sti_tx ="Recieved CDC reccomended STI prophalaxis" , abx_given = "Received any antibiotics", hiv_pep_kit_ordered_num = "HIV PEP ordered", hiv_labs = "Had indicated labs drawn if given HIV PEP", female_u55 = "Female under 55", pregnancy_test_ordered_num = "Pregnancy test ordered", prevent.preg = "Pregnancy prophalaxis ordered", sane_kit_YN = "SANE kit done", sane_kit_missed = "Under 120 hours and SANE kit not done", follow_up_at_discharge = "Has after discharge follow up") %>% tbl_summary(
    by = exposure.char,
    percent = "column",
    statistic =list(c(hiv_labs, prevent.preg, sti_tx, pregnancy_test_ordered_num) ~ "{n}" ) )
table.2 <- cohort.1 %>% select(pathway, advocate_offered, abx_given, sti_tx, hiv_pep_kit_ordered_num, hiv_labs, female_u55, pregnancy_test_ordered_num, prevent.preg, sane_kit_YN, sane_kit_missed, follow_up_at_discharge) %>% 
 set_variable_labels(advocate_offered = "Documentation of advocate contacted", sti_tx ="Recieved CDC reccomended STI prophalaxis" , abx_given = "Received any antibiotics", hiv_pep_kit_ordered_num = "HIV PEP ordered", hiv_labs = "Had indicated labs drawn if given HIV PEP", female_u55 = "Female under 55", pregnancy_test_ordered_num = "Pregnancy test ordered", prevent.preg = "Pregnancy prophalaxis ordered", sane_kit_YN = "SANE kit done", sane_kit_missed = "Under 120 hours and SANE kit not done", follow_up_at_discharge = "Has after discharge follow up") %>% tbl_summary(
    by = pathway,
    percent = "column",
    statistic =list(c(hiv_labs, prevent.preg, sti_tx, pregnancy_test_ordered_num) ~ "{n}" ) )
table2 <-
  tbl_merge(
    list(pp.table.2, table.2),
    tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")
  ) %>% as_gt()
table2
```

## Regression Outcomes

### Primary Outcome: _Advocate Contacted_

```{r advocate regression function}
advocate.regression<-function(data, exp){
  data$advocate_offered <- as_factor(data$advocate_offered )
  data$advocate_offered <- relevel(data$advocate_offered, ref= "No Documentation of Pt Advocate")
  model <-  glm(advocate_offered ~ exp + age + female + white + english + ipv, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```


All patients
```{r regression1, echo=FALSE}
cohort.1 <- cohort.1 %>% mutate(exposure = if_else(pathway == "Used Pathway", 1, 0))
tbl.reg.path.adv <-advocate.regression(cohort.1, exp = exposure)
tbl.reg.pp.adv <-advocate.regression(pp.cohort.2, exp = pp.cohort.2$exposure.num)

tbl.all.adv <- tbl_merge(list(tbl.reg.pp.adv, tbl.reg.path.adv), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate")
tbl.all.adv
```

Patients Under 120 Hours:

```{r under 120 regression, echo=FALSE}
pathway.u120 <- cohort.1 %>% filter(under120h == TRUE)
pp.u120 <- pp.cohort.2 %>% filter(under120h == TRUE)

tbl.reg.pp.adv.u120 <- advocate.regression(pp.u120)
tbl.reg.path.adv.u120 <- advocate.regression(pathway.u120)
tbl.reg.adv.u120 <- tbl_merge(list(tbl.reg.pp.adv.u120, tbl.reg.path.adv.u120), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate if Presented to ED <120 Hours Since Assault")
tbl.reg.adv.u120


pathway.u120$advocate_offered <- as_factor(pathway.u120$advocate_offered )
pathway.u120$advocate_offered <- relevel(pathway.u120$advocate_offered, ref= "No Documentation of Pt Advocate")
pathway.u120 <- pathway.u120 %>% mutate(exposure = if_else(pathway == "Used Pathway", 1, 0))
model.primary.120 <-  glm(advocate_offered ~ exposure + age + female + white + english + ipv, family = "binomial", data = pathway.u120)
primary.results.120 <- tbl_regression(model.primary.120, exponentiate = TRUE) %>% add_global_p() 

pp.u120 <- pp.u120 %>% mutate(exposure = exposure.num)
pp.u120$advocate_offered <- (as_factor(pp.u120$advocate_offered))
pp.u120$advocate_offered <- relevel(pp.u120$advocate_offered, ref= "No Documentation of Pt Advocate")
pp.model.primary.120 <-  glm(advocate_offered ~ exposure + age + female + white + english + ipv, family = "binomial", data = pp.u120)
pp.primary.results.120 <- tbl_regression(pp.model.primary.120, exponentiate = TRUE) %>% add_global_p() 

table.reg.u120 <- tbl_merge(list(pp.primary.results.120, primary.results.120), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate if Presented to ED <120 Hours Since Assault")
table.reg.u120
```
### Secondary Outcome: _Advocate Contacted/Offerred *IF* SANE Kit Done_
```{r under 120 SK done Reg, echo=FALSE}
pathway.u120.sk <- cohort.1 %>% filter(under120h == TRUE, sane_kit_YN == "Yes")
pp.u120.sk <- pp.cohort.2 %>%  filter(under120h == TRUE, sane_kit_YN == "Yes")
pathway.u120.sk$advocate_offered <- as_factor(pathway.u120.sk$advocate_offered )
pathway.u120.sk$advocate_offered <- relevel(pathway.u120.sk$advocate_offered, ref= "No Documentation of Pt Advocate")
pathway.u120.sk <- pathway.u120.sk %>% mutate(exposure = if_else(pathway == "Used Pathway", 1, 0))
model.primary.120.sk <-  glm(advocate_offered ~ exposure + age + female + white + english + ipv, family = "binomial", data = pathway.u120.sk)
primary.results.120.sk <- tbl_regression(model.primary, exponentiate = TRUE) %>% add_global_p() 

pp.u120.sk <- pp.u120.sk %>% mutate(exposure = exposure.num)
pp.u120.sk$advocate_offered <- (as_factor(pp.u120.sk$advocate_offered))
pp.u120.sk$advocate_offered <- relevel(pp.u120.sk$advocate_offered, ref= "No Documentation of Pt Advocate")
pp.model.primary.120.sk <-  glm(advocate_offered ~ exposure + age + female + white + english + ipv, family = "binomial", data = pp.u120.sk)
pp.primary.results.120.sk <- tbl_regression(pp.model.primary.120.sk, exponentiate = TRUE) %>% add_global_p() 

table.reg.sk120 <- tbl_merge(list(pp.primary.results.120.sk, primary.results.120.sk), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate if SANE Kit Done")
table.reg.sk120
```

### Secondary Outcome: _For Women _

