---
title: "SA Project Current Results Page"
author: "Raffi Sherak"
date: "`r Sys.Date()`"
output: html_document
---

```{r include=FALSE}
library(readr)
library(tidyverse)
library(lubridate)
library(gtsummary)
library(gt)
library(parsedate)
library(janitor)
library(labelled)
library(parameters)
library(survival)
library(ggsurvfit)
library(table1)
library(hms)
all_pts <- read_csv("~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/SA_pts_reformatted.csv")
# set TZ to east coast standard
time_zone <- "America/New_York"
#pathway went live on 7/13/21
pathway_start <- mdy("7/13/21", tz = time_zone)
#Story board notification went live on 9/8/21
sb_start <- mdy("9/8/21", tz = time_zone)
day.arrival.start <- hms::as_hms("06:00:00")
night.arrival.start <- hms::as_hms("18:00:00")
```

```{r outcome variables, include=FALSE}
# making outcome variable for if correct STI tx: CTX, azithromycin or doxy (and flagyl if female) are ordered 
all_pts <- all_pts %>% mutate(
  azithro_or_doxy = case_when(
    azithromycin_ordered_num | doxycycline_ordered_num == 1 ~ 1,
    azithromycin_ordered_num == 0 &
      doxycycline_ordered_num == 0 ~ 0,
    .default = 0
  )
) %>% mutate(
  sti_tx = case_when(
    gender == "Male" &
      ceftriaxone_ordered_num == 1 & azithro_or_doxy == 1 ~ 1,
    gender == "Male" &
      ceftriaxone_ordered_num | azithro_or_doxy == 0  ~ 0,
    gender == "Female" &
      ceftriaxone_ordered_num == 1 &
      azithro_or_doxy == 1 &
      flagyl_or_metronidazole_ordered_num == 1 ~ 1,
    gender == "Female" &
      ceftriaxone_ordered_num |
      azithro_or_doxy |
      flagyl_or_metronidazole_ordered_num == 0 ~ 0,
    .default = 0
  ),
  chem_ordered = case_when(
    cmp_ordered_yn == "Y" | bmp_ordered_yn == "Y" ~ 1,
    cmp_ordered_yn == "N" & bmp_ordered_yn == "N" ~ 0,
    .default = NA
  ),
  abx_given = case_when(
    ceftriaxone_ordered_num == 0 &
      azithro_or_doxy == 0 &
      flagyl_or_metronidazole_ordered_num == 0 ~ 0,
    ceftriaxone_ordered_num == 1 |
      azithro_or_doxy == 1 |
      flagyl_or_metronidazole_ordered_num == 1 ~ 1
  ),
  lfts_ordered = case_when(
    cmp_ordered_yn == "Y" | lft_ordered_yn == "Y" ~ 1,
    cmp_ordered_yn == "N" & lft_ordered_yn == "N" ~ 0,
    .default = NA
  )
) %>% mutate(
  hiv_labs = case_when(
    hiv_pep_kit_ordered_num == 1 &
      chem_ordered == 1 & lfts_ordered == 1 ~ 1,
    hiv_pep_kit_ordered_num == 1 &
      (chem_ordered == 0| lfts_ordered == 0) ~ 0,
    .default = 0
  ),
  prevent.preg = case_when(
    plan_b_or_levonorgestrel_ordered_num == 1 | ulipristal_ordered_num == 1 ~ 1,
    plan_b_or_levonorgestrel_ordered_num == 0 & ulipristal_ordered_num == 0 ~ 0,
    .default = NA
  ),
  advocate_offered = case_when(
    patient_advocate_called == 1 | patient_advocate_called == 3 ~ "Advocate Offered",
    patient_advocate_called == 0 | patient_advocate_called == 2 ~ "No Documentation of Pt Advocate",
    .default = NA
  ),
  sane_kit_YN = case_when(
    sane_kit_done == 0 ~ "No",
    sane_kit_done == 1 ~ "Yes",
    sane_kit_done == 2 ~ "Offered, but declined",
    sane_kit_done == 3 ~ "Outside 120 hr Window",
    sane_kit_done == 4 ~ "Not done due to concurrent psychiatric concerns"
  ),
  sane_kit_missed = case_when(
    sane_kit_done == 0 ~ "SANE kit not done/documented",
    sane_kit_done %in% c(1,2,3) ~ "SANE kit done/not indicated",
    sane_kit_done == 4 ~ "Not done due to concurrent psychiatric concerns"
  )
) %>% 
  mutate(
    tbl_sti_tx = case_when(
      sti_tx == 1 & abx_given == 1 ~ 1,
      sti_tx == 0 & abx_given == 1 ~ 0,
      .default = NA
    ),
    tbl_hiv_labs = case_when(
      hiv_pep_kit_ordered_num == 1 & hiv_labs == 1 ~ 1,
       hiv_pep_kit_ordered_num == 1 & hiv_labs == 0 ~ 0,
      .default = NA
    ),
    tbl_preg_test = case_when(
      female_u55 == 1 & pregnancy_test_ordered_num == 1 ~ 1,
      female_u55 == 1 & pregnancy_test_ordered_num == 0 ~ 0,
      .default = NA
    ),
      tbl_prevent_preg = case_when(
      female_u55 == 1 & prevent.preg == 1 ~ 1,
      female_u55 == 1 & prevent.preg == 0 ~ 0,
      .default = NA
      ),
    under120h = case_when(
    time_since_sexual_assault_if_number_k_is_y == 0 |  time_since_sexual_assault_if_number_k_is_y == 1 ~ TRUE,
    time_since_sexual_assault_if_number_k_is_y == 2 |  time_since_sexual_assault_if_number_k_is_y == 3 ~ FALSE,
    .default = NA
  ),
  english = case_when(
    patient_language == "English" ~ 1,
    is.na(patient_language) ~ NA,
    .default = 0
  ),
  ambulance = if_else(method_of_arrival == 1, 1, 0),
  relationship_with_patient = factor(relationship_with_patient, levels = c(0,1,2,3,4,NA), labels = c("Unknown","Aqauintance", "Family member", "Stranger", "Intimate Partner", NA), exclude = NULL, ordered = FALSE ),
  insurance_3 = case_when(
    insurance == "Private Insurance" ~ "Private",
    insurance %in% c("Medicaid", "Medicare", "Sexual Assault") ~ "Public",
    insurance == "Uninsured/Self-Pay" ~ "Uninsured"
  ),
  SA_insurance = if_else(
    insurance == "Sexual Assault", 1, 0
  )
  ) %>% 
    mutate(relationship_4_with_pt = case_when(
    relationship_with_patient == "Family member" ~ "Family",
    relationship_with_patient == "Aqauintance" ~ "Aquaintaince",
    relationship_with_patient == "Intimate Partner" ~ "Intimate Partner",
    relationship_with_patient == "Unknown" |relationship_with_patient == "Stranger" ~ "Stranger/Unknown"
  )) %>% 
  mutate(arrive_time = as_hms(arrive_dt)) %>% 
  mutate(day_night = case_when(
    arrive_time >= day.arrival.start & arrive_time <= night.arrival.start ~ "Day",
    arrive_time < day.arrival.start | arrive_time > night.arrival.start ~ "Night",
    .default = "ERROR"
  ))
all_pts$insurance_3 <- as_factor(all_pts$insurance_3)
all_pts$insurance_3 <- relevel(all_pts$insurance_3, ref = "Public")
```

# pathway creating cohorts

###First creation of cohort by removing:  
_-patients before story board start date 2021-09-08_  
_-minors_   
_-excluded patients_
```{r echo=FALSE}
cohort.1 <- all_pts %>% filter(ed_arrival_date > sb_start) %>% filter(age > 17)
excluded_patients <- cohort.1  %>% filter(!is.na(exclude))
cohort.2 <- cohort.1  %>% filter(is.na(exclude))
excluded_patients <- excluded_patients %>% add_value_labels(reason_to_exclude = c( "Seen earlier" = 1 , "Patient reports not being assaulted" = 2, "Psych" = 3, "not excluded" = 4, "Eloped" = 5)) %>% to_factor()
excluded_patients %>% group_by(reason_to_exclude) %>% summarise(n=n())
n_excluded <-n_distinct(excluded_patients$pat_enc_csn_id, na.rm=TRUE) %>% as.character()
cat("-", n_excluded, "patients were excluded based on chart review.")
number_of_minors <-all_pts %>% filter(ed_arrival_date > sb_start) %>% filter(age < 18)
number_of_minors <- n_distinct(number_of_minors$pat_enc_csn_id, na.rm = TRUE) %>% as.character()
cat("  ", number_of_minors, "patients under 18 YO excluded")
rm(n_excluded, number_of_minors)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
table.1 <- cohort.2 %>% 
  select(pathway, age, female, race_bwo, under120h, day_night, english, ambulance, insurance, relationship_with_patient) %>% 
  set_variable_labels(age = "Age",  female = "Female", race_bwo = "Race", under120h = "Presented within 120 of assault", ambulance = "Arrived by EMS", english = "English speaking", insurance = "Insurance", relationship_with_patient = "Relation of assailant to patient", day_night = "Time of arrival") %>% 
  tbl_summary(
    by = pathway,
    missing = "ifany", 
    percent = "column",
    statistic = (age ~ "{median} ({p25}, {p75})")
  ) %>% 
  add_p() %>% separate_p_footnotes() %>%  as_gt() 
table.1

```
```{r echo=FALSE, message=FALSE, warning=FALSE}
table.2 <- cohort.2 %>% select(pathway, advocate_offered, abx_given, sti_tx, hiv_pep_kit_ordered_num, hiv_labs, female_u55, pregnancy_test_ordered_num, prevent.preg, sane_kit_YN, sane_kit_missed, follow_up_at_discharge) %>% 
 set_variable_labels(advocate_offered = "Documentation of advocate contacted", sti_tx ="Recieved CDC reccomended STI prophalaxis" , abx_given = "Received any antibiotics", hiv_pep_kit_ordered_num = "HIV PEP ordered", hiv_labs = "Had indicated labs drawn if given HIV PEP", female_u55 = "Female under 55", pregnancy_test_ordered_num = "Pregnancy test ordered", prevent.preg = "Pregnancy prophalaxis ordered", sane_kit_YN = "SANE kit done", sane_kit_missed = "Under 120 hours and SANE kit not done", follow_up_at_discharge = "Has after discharge follow up") %>% tbl_summary(
    by = pathway,
    percent = "column",
    statistic =list(c(hiv_labs, prevent.preg, sti_tx, pregnancy_test_ordered_num) ~ "{n}" ) ) %>% as_gt()
table.2
```

## Primary outcome- ADVOCATE CONTACTED
```{r}
cohort.2$race_bwo <- as_factor(cohort.2$race_bwo)
cohort.2$race_bwo <- relevel(cohort.2$race_bwo, ref= "White")
cohort.2$advocate_offered <- (as_factor(cohort.2$advocate_offered))
cohort.2$advocate_offered <- relevel(cohort.2$advocate_offered, ref= "No Documentation of Pt Advocate")
model.primary <-  glm(advocate_offered ~ pathway + age + female + white + SA_insurance + english,  family = "binomial", data = cohort.2)
primary.results <- tbl_regression(model.primary, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header( "Odds of documentation of offering call to PT advocate") 
summary(model.primary)
primary.results
```

### Primary outcome, sub-outcome- ADVOCATE CONTACTED *IF* SANE KIT DONE

```{r}
cohort.2$race_bwo <- as_factor(cohort.2$race_bwo)
cohort.2$race_bwo <- relevel(cohort.2$race_bwo, ref= "White")
cohort.2$advocate_offered <- (as_factor(cohort.2$advocate_offered))
cohort.2$advocate_offered <- relevel(cohort.2$advocate_offered, ref= "No Documentation of Pt Advocate")
cohort.2.2 <- cohort.2 %>% filter(sane_kit_done == 1) #156 patients
model.primary.2 <-  glm(advocate_offered ~ pathway + age + female + white,  family = "binomial", data = cohort.2.2)
primary.results.2 <- tbl_regression(model.primary.2, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header( "Odds of documentation of offering call to PT advocate IF SANE Kit Done") 
summary(model.primary.2)
primary.results.2
```

## Secondary Outcome: SANE Kit Done/ offered if eligible
restricted to patients presenting within 120 hours
*this regression has issues with some predictors due to small sample size. Controlling for sex leads to problem since all 12 men had SANE kit offered. controlling for english vs other language also has problem as all 11 non-English speakers had sane kit offered to them. same for all 2 patients that were assualted by family members (all offerred kit)* _we will need to consider which confoudners we control for/ if we care about the effect estimates for confounding factors_
```{r}
#removing patients where they presented > 120 hours into stay OR did not qualify for sane kit because of concurrent psych issues.
cohort.3 <- cohort.2 %>% filter(under120h == TRUE, sane_kit_missed != "Not done due to concurrent psychiatric concerns") %>% 
  mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
cohort.3$race_bwo <- as_factor(cohort.3$race_bwo)
cohort.3$race_bwo <- relevel(cohort.3$race_bwo, ref= "White")
cohort.3$sane_kit_offered <- as_factor(cohort.3$sane_kit_offered)
cohort.3$sane_kit_offered <- relevel(cohort.3$sane_kit_offered, ref = "No")
cohort.3$relationship_4_with_pt <- as_factor(cohort.3$relationship_4_with_pt)
cohort.3$relationship_4_with_pt <- relevel(cohort.3$relationship_4_with_pt, ref = "Stranger/Unknown")
model.secondary.1 <-  glm(sane_kit_offered ~ pathway + age + white + insurance_3,  family = "binomial", data = cohort.3)
secondary.results.1 <- tbl_regression(model.secondary.1, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header( "Odds of Offering SANE Kit if Eligible") 
summary(model.secondary.1)
secondary.results.1
```

Pregnancy related outcomes
*note- used 120 hour as threshold for eligibility for EC since ulipristol can be used up to 120 hours*
```{r}
tertiary.cohort <- cohort.2 %>%  filter(female_u55 == 1)
quatrinary.cohort <- tertiary.cohort %>% filter(under120h = TRUE)
model.tertiary <-  glm(pregnancy_test_ordered_num ~ pathway + age + race_bwo + english + ambulance, family = "binomial", data = tertiary.cohort)
summary(model.tertiary)
tertiary.results <- tbl_regression(model.tertiary, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Secondary Outcome (did women under 55 get preg test?)")
tertiary.results
model.quatro <-  glm(prevent.preg ~ pathway + age + white +  english + ambulance, family = "binomial", data = quatrinary.cohort)
summary(model.quatro)
quatro.results <- tbl_regression(model.quatro, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Secondary Outcome (did women under 55 have pregnancy prevention ordered?)")
quatro.results
```

## Secondary Outcome: Correct STI tx if given *any* antibiotics
Meaning: Women got Metronidizole + CTX + Azithromycin or Doxy
        only one male patient received incorrect abx for STI treatment causing 0 cell problem so had to restrict to female patients
```{r}
#need to first restrict to patients who got any antibiotics
abx.cohort <- cohort.2 %>% filter(abx_given == 1) # 184 pts
model.sti.tx <- glm(tbl_sti_tx ~ pathway + age + white + english + relationship_4_with_pt, family = "binomial", data = abx.cohort)
summary(model.sti.tx)
sti.model.results <- tbl_regression(model.sti.tx, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Odds that Correct STI Tx was given if pt received ABX")
sti.model.results
```

## Secondary Outcome: Correct labs ordered if patient given PEP
restricted to those presenting within 72 hours
```{r}
cohort.u72 <- cohort.2 %>% filter(time_since_sexual_assault_if_number_k_is_y == 0) #restricting to those <72 hours. 206 patients. 
cohort.u72.pep <- cohort.u72 %>% filter(hiv_pep_kit_ordered_num ==1) #72 patients only
model.hiv.labs <-  glm(hiv_labs ~ pathway + age + female + race_bwo, family = "binomial", data = cohort.u72.pep)
summary(model.hiv.labs)
hiv.labs.results <- tbl_regression(model.hiv.labs, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Secondary Outcome (did patients who got HIV PEP have LFTs ordered?)")
hiv.labs.results

```

# creating pre-post cohorts

###First creation of cohort by removing:  
_-minors_   
_-excluded patients_
_patients between 7/13/21 and 9/8/21_

```{r}
between_pts <- all_pts %>% filter(between == 1)
n_between <- n_distinct(between_pts$pat_enc_csn_id, na.rm=TRUE) %>% as.character()
pp.cohort.1 <- all_pts %>% filter(between == 0) %>% filter(age > 17)
excluded_patients <- pp.cohort.1  %>% filter(!is.na(exclude))
pp.cohort.2 <- pp.cohort.1  %>% filter(is.na(exclude))
excluded_patients <- excluded_patients %>% add_value_labels(reason_to_exclude = c( "Seen earlier" = 1 , "Patient reports not being assaulted" = 2, "Psych" = 3, "not excluded" = 4, "Eloped" = 5)) %>% to_factor()
excluded_patients %>% group_by(reason_to_exclude) %>% summarise(n=n())
n_excluded <-n_distinct(excluded_patients$pat_enc_csn_id, na.rm=TRUE) %>% as.character()
cat(" ", n_between, "patients who arrived between 7/13/21 and 9/8/21 were excluded")
cat("-", n_excluded, "patients were excluded based on chart review.")
number_of_minors <-all_pts %>% filter(between == 0) %>% filter(age < 18)
number_of_minors <- n_distinct(number_of_minors$pat_enc_csn_id, na.rm = TRUE) %>% as.character()
cat("  ", number_of_minors, "patients under 18 YO excluded")
rm(n_excluded, number_of_minors, n_between)
```

# Begin Pre 7/13/21 vs Post 9/8/21 analysis
```{r echo=FALSE, message=FALSE, warning=FALSE}
pp.table.1 <- pp.cohort.2 %>% 
  select(exposure.char, pathway, age, female, race_bwo, under120h, english, ambulance, insurance, relationship_with_patient) %>% 
  set_variable_labels(age = "Age",  female = "Female", race_bwo = "Race", under120h = "Presented within 120 of assault", ambulance = "Arrived by EMS", english = "English speaking", insurance = "Insurance", relationship_with_patient = "Relation of assailant to patient") %>% 
  tbl_summary(
    by = exposure.char,
    missing = "ifany", 
    percent = "column",
    statistic = (age ~ "{median} ({p25}, {p75})")
  ) %>% 
  add_p() %>% separate_p_footnotes() %>%  as_gt() 
pp.table.1

```
```{r echo=FALSE, message=FALSE, warning=FALSE}
pp.table.2 <- pp.cohort.2 %>% select(exposure.char, advocate_offered, abx_given, sti_tx, hiv_pep_kit_ordered_num, hiv_labs, female_u55, pregnancy_test_ordered_num, prevent.preg, sane_kit_YN, sane_kit_missed, follow_up_at_discharge) %>% 
 set_variable_labels(advocate_offered = "Documentation of advocate contacted", sti_tx ="Recieved CDC reccomended STI prophalaxis" , abx_given = "Received any antibiotics", hiv_pep_kit_ordered_num = "HIV PEP ordered", hiv_labs = "Had indicated labs drawn if given HIV PEP", female_u55 = "Female under 55", pregnancy_test_ordered_num = "Pregnancy test ordered", prevent.preg = "Pregnancy prophalaxis ordered", sane_kit_YN = "SANE kit done", sane_kit_missed = "Under 120 hours and SANE kit not done", follow_up_at_discharge = "Has after discharge follow up") %>% tbl_summary(
    by = exposure.char,
    percent = "column",
    statistic =list(c(hiv_labs, prevent.preg, sti_tx, pregnancy_test_ordered_num) ~ "{n}" ) ) %>% as_gt()
pp.table.2
```

# Pre/Post analysis Primary outcome- ADVOCATE CONTACTED
```{r}
pp.cohort.2$race_bwo <- as_factor(pp.cohort.2$race_bwo)
pp.cohort.2$race_bwo <- relevel(pp.cohort.2$race_bwo, ref= "White")
pp.cohort.2$advocate_offered <- (as_factor(pp.cohort.2$advocate_offered))
pp.cohort.2$advocate_offered <- relevel(pp.cohort.2$advocate_offered, ref= "No Documentation of Pt Advocate")
pp.model.primary <-  glm(advocate_offered ~ exposure.num + age + female + white + insurance_3 + english + relationship_4_with_pt,  family = "binomial", data = pp.cohort.2)
pp.primary.results <- tbl_regression(pp.model.primary, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header( "Odds of documentation of offering call to PT advocate") 
summary(pp.model.primary)
pp.primary.results
```

### Primary outcome, sub-outcome- ADVOCATE CONTACTED *IF* SANE KIT DONE

```{r}
pp.cohort.2$race_bwo <- as_factor(pp.cohort.2$race_bwo)
pp.cohort.2$race_bwo <- relevel(pp.cohort.2$race_bwo, ref= "White")
pp.cohort.2$advocate_offered <- (as_factor(pp.cohort.2$advocate_offered))
pp.cohort.2$advocate_offered <- relevel(pp.cohort.2$advocate_offered, ref= "No Documentation of Pt Advocate")
pp.cohort.2.2 <- pp.cohort.2 %>% filter(sane_kit_done == 1) #156 patients
pp.model.primary.2 <-  glm(advocate_offered ~ exposure.num + age + female + white + insurance_3 + english,  family = "binomial", data = pp.cohort.2.2)
pp.primary.results.2 <- tbl_regression(pp.model.primary.2, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header( "Odds of documentation of offering call to PT advocate") 
summary(pp.model.primary.2)
pp.primary.results.2
```

## Secondary Outcome: SANE Kit Done/ offered if eligible
restricted to patients presenting within 120 hours
*this regression has issues with some predictors due to small sample size. Controlling for sex leads to problem since all 12 men had SANE kit offered. controlling for english vs other language also has problem as all 11 non-English speakers had sane kit offered to them. same for all 2 patients that were assualted by family members (all offerred kit)* _we will need to consider which confoudners we control for/ if we care about the effect estimates for confounding factors_
```{r}
#removing patients where they presented > 120 hours into stay OR did not qualify for sane kit because of concurrent psych issues.
pp.cohort.3 <- pp.cohort.2 %>% filter(under120h == TRUE, sane_kit_missed != "Not done due to concurrent psychiatric concerns") %>% 
  mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
pp.cohort.3$race_bwo <- as_factor(pp.cohort.3$race_bwo)
pp.cohort.3$race_bwo <- relevel(pp.cohort.3$race_bwo, ref= "White")
pp.cohort.3$sane_kit_offered <- as_factor(pp.cohort.3$sane_kit_offered)
pp.cohort.3$sane_kit_offered <- relevel(pp.cohort.3$sane_kit_offered, ref = "No")
pp.cohort.3$relationship_4_with_pt <- as_factor(pp.cohort.3$relationship_4_with_pt)
pp.cohort.3$relationship_4_with_pt <- relevel(pp.cohort.3$relationship_4_with_pt, ref = "Stranger/Unknown")
pp.model.secondary.1 <-  glm(sane_kit_offered ~ exposure.num + age + race_bwo + insurance_3,  family = "binomial", data = pp.cohort.3)
pp.secondary.results.1 <- tbl_regression(pp.model.secondary.1, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header( "Odds of Offering SANE Kit if Eligible") 
summary(pp.model.secondary.1)
pp.secondary.results.1
```

## Pregnancy related outcomes
*note- used 120 hour as threshold for eligibility for EC since ulipristol can be used up to 120 hours*
```{r}
pp.tertiary.cohort <- pp.cohort.2 %>%  filter(female_u55 == 1)
pp.quatrinary.cohort <- pp.tertiary.cohort %>% filter(under120h = TRUE)
model.tertiary <-  glm(pregnancy_test_ordered_num ~ pathway + age + white + english + ambulance, family = "binomial", data = pp.tertiary.cohort)
summary(model.tertiary)
pp.tertiary.results <- tbl_regression(model.tertiary, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Secondary Outcome (did women under 55 get preg test?)")
pp.tertiary.results
pp.model.quatro <-  glm(prevent.preg ~ exposure.num + age + white +  english + ambulance, family = "binomial", data = pp.quatrinary.cohort)
summary(pp.model.quatro)
pp.quatro.results <- tbl_regression(pp.model.quatro, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Secondary Outcome (did women under 55 have pregnancy prevention ordered?)")
pp.quatro.results
```

## Secondary Outcome: Correct STI tx if given *any* antibiotics
Meaning: Women got Metronidizole + CTX + Azithromycin or Doxy
        only one male patient received incorrect abx for STI treatment causing 0 cell problem so had to restrict to female patients
```{r}
#need to first restrict to patients who got any antibiotics
pp.abx.cohort <- pp.cohort.2 %>% filter(abx_given == 1) # 184 pts
pp.model.sti.tx <- glm(tbl_sti_tx ~ exposure.num + age + white + english + relationship_4_with_pt, family = "binomial", data = pp.abx.cohort)
summary(pp.model.sti.tx)
pp.sti.model.results <- tbl_regression(pp.model.sti.tx, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Odds that Correct STI Tx was given if pt received ABX")
pp.sti.model.results
```

## Secondary Outcome: Correct labs ordered if patient given PEP
restricted to those presenting within 72 hours
```{r}
pp.cohort.u72 <- pp.cohort.2 %>% filter(time_since_sexual_assault_if_number_k_is_y == 0) #restricting to those <72 hours. 206 patients. 
pp.cohort.u72.pep <- pp.cohort.u72 %>% filter(hiv_pep_kit_ordered_num ==1) #72 patients only
pp.model.hiv.labs <-  glm(hiv_labs ~ exposure.num + age + female + race_bwo, family = "binomial", data = pp.cohort.u72.pep)
summary(pp.model.hiv.labs)
pp.hiv.labs.results <- tbl_regression(pp.model.hiv.labs, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Secondary Outcome (did patients who got HIV PEP have LFTs ordered?)")
pp.hiv.labs.results

```

# Supplemental Analysis: Day (6a to 6p arrivals) VS Night (6p to 6a arrivals)

```{r}
d.n.cohort <- all_pts %>% filter(age > 17) %>% filter(is.na(exclude)) %>% mutate(advocate_present = case_when(
    patient_advocate_present == 1 ~ TRUE,
    patient_advocate_present == 0 ~ FALSE,
    .default = NA))
supp.table.1 <- d.n.cohort %>% 
  select(day_night, age, female, race_bwo, under120h, english, ambulance, insurance, relationship_with_patient, advocate_present,advocate_offered, sane_kit_YN) %>% 
  set_variable_labels( day_night = "Time of arrival", age = "Age",  female = "Female", race_bwo = "Race", under120h = "Presented within 120 of assault", ambulance = "Arrived by EMS", english = "English speaking", insurance = "Insurance", relationship_with_patient = "Relation of assailant to patient", sane_kit_YN = "SANE kit done?") %>% 
  tbl_summary(
    by = day_night,
    missing = "ifany", 
    percent = "column",
    statistic = (age ~ "{median} ({p25}, {p75})")
  ) %>% 
  add_p() %>% separate_p_footnotes() %>%  as_gt() 
supp.table.1

```

```{r}
d.n.cohort$advocate_offered <- (as_factor(d.n.cohort$advocate_offered))
d.n.cohort$advocate_offered <- relevel(d.n.cohort$advocate_offered, ref= "No Documentation of Pt Advocate")
sup.mod.1 <-  glm(advocate_offered ~ day_night + age + female + white + SA_insurance + english,  family = "binomial", data = d.n.cohort)
sup.primary.results <- tbl_regression(sup.mod.1, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header( "Odds of documentation of offering call to PT advocate") 
sup.primary.results
```
```{r}
advocate_showed_cohort <- d.n.cohort %>% filter(advocate_offered == "Advocate Offered")
sup.mod.2 <-  glm(advocate_present ~ day_night + age + female + white,  family = "binomial", data = d.n.cohort)
sup.primary.results.2 <- tbl_regression(sup.mod.2, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header( "Odds of advocate being present") 
sup.primary.results.2
```

