---
title: "SA Paper 1 Analysis"
output:
  html_document: 
    toc: yes
    theme: journal
    keep_md: yes
    code_folding: hide
    fig_width: 9
    fig_height: 6
    df_print: default
  html_notebook:
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

## Prep Code

```{r Initial Data and Package Prep, echo=TRUE, message=FALSE, warning=FALSE}
library(readr)
library(logistf)
library(tidyverse)
library(lubridate)
library(gtsummary)
library(gt)
library(parsedate)
library(janitor)
library(labelled)
library(parameters)
library(survival)
library(ggsurvfit)
library(table1)
library(hms)
library(readxl)
library(ggborderline)
theme_gtsummary_journal(journal = "jama")
theme_gtsummary_compact()
load(
  "~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/all_pts.RData"
)
# set TZ to east coast standard
time_zone <- "America/New_York"
#pathway went live on 7/13/21
pathway_start <- mdy("7/13/21", tz = time_zone)
#Story board notification went live on 9/8/21
sb_start <- mdy("9/8/21", tz = time_zone)
day.arrival.start <- hms::as_hms("03:00:00")
night.arrival.start <- hms::as_hms("15:00:00")
all_pts$insurance_3 <- as_factor(all_pts$insurance_3)
all_pts$insurance_3 <- relevel(all_pts$insurance_3, ref = "Public")
all_pts <- all_pts %>% mutate(
    race_eth = case_when(
      patient_ethnicity == "Hispanic or Latina/o/x" ~ "Hispanic or Latina/o/x",
      patient_race == "Black or African American" ~ "Non-Hispanic Black",
      patient_race == "White" ~ "Non-Hispanic White",
      patient_ethnicity != "Hispanic or Latina/o/x" &
        patient_race != "Black or African American" &
        patient_race != "White" ~ "Other",
      .default = patient_race
    )
  ) %>% 
  mutate(
    race_eth_num = case_when(
      race_eth == "Non-Hispanic White" ~ 0,
      race_eth == "Non-Hispanic Black" ~ 1,
      race_eth == "Hispanic or Latina/o/x" ~ 3,
      race_eth == "Other" ~ 4
    )
  ) %>% 
  set_value_labels(
    race_eth_num = c(
      "Non-Hispanic White" = 0,
      "Non-Hispanic Black" = 1,
      "Hispanic or Latina/o/x" = 3,
      "Other" = 4
    )
  )
all_pts$race_eth_num <- to_factor(all_pts$race_eth_num, ordered = FALSE)
all_excluded <- all_pts %>%
  mutate(exclude = case_when(age < 18 ~ 1,
                             between == 1 ~ 1,
                             sane_kit_done == 4 ~ 1,
                             exclude == 1 ~ 1)) %>%
  mutate(
    reason_to_exclude = case_when(
      age < 18 ~ 8,
      is.na(reason_to_exclude) & between == 1 ~ 7,
      is.na(reason_to_exclude) & sane_kit_done == 4 ~ 3,
      is.na(reason_to_exclude) ~ 6,
      .default = reason_to_exclude
    )
  ) %>% add_value_labels(
    reason_to_exclude = c(
      "Seen earlier" = 1 ,
      "Patient reports not being assaulted" = 2,
      "Psych" = 3,
      "not excluded" = 4,
      "Eloped" = 5,
      "NA/Not Listed" = 6,
      "Between Period" = 7,
      "Under 18 YO" = 8
    )
  ) %>% to_factor()
all_excluded <- all_excluded %>% filter(exclude == 1)
excluded_plot <-
  all_excluded %>% ggplot(aes(x = reason_to_exclude)) + geom_bar(fill = "darkred") + geom_text(stat =
                                                                                                 'count', aes(label = after_stat(count)), vjust = -0.5, size = 3.5) + theme_minimal() + labs(x = "Reason to Exclude", y = "Count", title = "Excluded Patients by Reason") + theme(axis.text.x = element_text(angle = 35, vjust = .6, hjust= .8))

excluded_plot

all_excluded %>% group_by(reason_to_exclude) %>% summarise(n = n()) %>% print()

number_of_minors <-
  all_excluded %>% filter(age < 18) #changed it so age is first exclusion criteria
number_of_minors <-
  n_distinct(number_of_minors$pat_enc_csn_id, na.rm = TRUE) %>% as.character()
cat("  ", number_of_minors, "patients under 18 YO excluded")
n_excluded <-
  all_excluded %>% filter(
    reason_to_exclude %in% c(
      "Seen earlier",
      "Patient reports not being assaulted",
      "Psych",
      "Eloped",
      "NA/Not Listed"
    )
  )
n_excluded <-
  n_distinct(n_excluded$pat_enc_csn_id, na.rm = TRUE) %>% as.character()
n_between <-
  all_excluded %>% filter(reason_to_exclude == "Between Period")
n_between <-
  n_distinct(n_between$pat_enc_csn_id, na.rm = TRUE) %>% as.character()

cat("-", n_excluded, "patients were excluded based on chart review.")
cat(" ",
    n_between,
    "patients who arrived between 7/13/21 and 9/8/21 were excluded")
rm(n_excluded, number_of_minors, n_between)
#pre-post cohort
pp.cohort.1 <-
  all_pts %>% filter(between == 0) %>% filter(age > 17) %>% filter(is.na(exclude), sane_kit_done != 4) %>% mutate(exposure.tab = exposure.char)
#pathway v no pathway cohort
cohort.1 <-
  all_pts %>% filter(ed_arrival_date > sb_start) %>% filter(age > 17) %>% filter(is.na(exclude)) %>% mutate(exposure.tab = pathway)
#pre vs no pathway cohort
pp.cohort.2 <- pp.cohort.1 %>% filter(agile_md_used_num != 1)
```

942 patient encounters from 2019-12-31 to 2022-12-24\
In order of exclusion: age -\> chart review -\> between period

## Table 1 and 2

```{r tbl 1 fxn, echo=FALSE, message=FALSE, warning=FALSE}
tbl.one.fxn <- function(df) {
  x <- df %>% select(exposure.tab,
                     age,
                     female,
                     race_eth_num,
                     under120h,
                     u72,
                     english,
                     ambulance,
                     intoxicated,
                     Psych,
                     ipv) %>%
    set_variable_labels(
      age = "Age",
      female = "Female",
      race_eth_num = "Race",
      under120h = "Presented within 120h of assault",
      u72 = "Presented within 72h of assault",
      ambulance = "Arrived by EMS",
      english = "English speaking",
      ipv = "Assailant was Intimate Partner",
      intoxicated = "Diagnosis of Intoxication",
      Psych = "Psychiatric Diagnosis"
    ) %>%
    tbl_summary(
      by = exposure.tab,
      missing = "ifany",
      percent = "column",
      statistic = (age ~ "{median} ({p25}, {p75})")
    ) %>%
    add_p() %>% separate_p_footnotes()
  return(x)
}
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
pp.cohort.1$exposure.tab <- factor(pp.cohort.1$exposure.tab, levels=c("Post-intervention", "Pre-intervention"))
cohort.1$exposure.tab <- factor(cohort.1$exposure.tab, levels = c("Used Pathway", "Didn't Use Pathway"))
pp.table.1 <- tbl.one.fxn(pp.cohort.1) %>% add_overall()
table.1 <- tbl.one.fxn(cohort.1)
  table1 <-
    tbl_merge(
      list(pp.table.1, table.1),
      tab_spanner = c("**Post v. Pre**", "**Pathway v. No Pathway**")
    ) %>% as_gt()
table1
```

```{r tbl 2 fxns, echo=FALSE, message=FALSE, warning=FALSE}
#note to self-> make it so males, over55 are NA so table can be fixed for proper %
tbl.two.fxn <- function(data) {
  x <- data %>% mutate(
    tbl_sane_kit_u120 = case_when(
      under120h == TRUE & sane_kit_done == 1 ~ 1,
      under120h == TRUE & sane_kit_done != 1 ~ 0,
      .default = NA
    ),advocate_off_num = case_when(
      advocate_offered == "Advocate Offered" ~ 1,
      advocate_offered ==  "No Documentation of Pt Advocate" ~ 0,
      is.na(advocate_offered) ~ NA,
      .default = NA
    ),
  ) %>%
    select(
      exposure.tab,
      advocate_off_num,
      abx_given,
      tbl_prevent_hiv,
      female_u55,
      tbl_preg_test,
      tbl_prevent_preg,
      sane_ED,
      sane_kit_YN,
      tbl_sane_kit_u120,
      follow_up_at_discharge
    ) %>%
    set_variable_labels(
      advocate_off_num = "Documentation of advocate offerred",
      abx_given = "PEP antibiotics ordered",
      tbl_prevent_hiv = "HIV PEP ordered (if < 72h from assault",
      female_u55 = "Female under 55",
      tbl_preg_test = "Pregnancy test ordered",
      tbl_prevent_preg = "Pregnancy prophalaxis ordered",
      sane_ED = "ED with SANE program",
      sane_kit_YN = "SANE kit done",
      tbl_sane_kit_u120 = "Under 120 hours and SANE kit done",
      follow_up_at_discharge = "Has after discharge follow up"
    ) %>% tbl_summary(
      by = exposure.tab,
      percent = "column",
      missing = "no",
      statistic = contains("tbl") ~ "{n}/{N_nonmiss} ({p}%)"
    ) %>% add_p(test = list(sane_kit_YN ~ 'fisher.test' , follow_up_at_discharge ~ 'chisq.test')) %>% separate_p_footnotes()
  return(x)
}

```

```{r tables, echo=FALSE, message=FALSE, warning=FALSE}
pp.cohort.1$exposure.tab <- factor(pp.cohort.1$exposure.tab, levels=c("Pre-intervention", "Post-intervention"))
pp.table.2 <-tbl.two.fxn(pp.cohort.1) %>% add_overall()
cohort.1$exposure.tab <- factor(cohort.1$exposure.tab, levels = c("Used Pathway", "Didn't Use Pathway"))
path.table.2 <-tbl.two.fxn(cohort.1)
 table.2 <-tbl_merge(
    list(pp.table.2, path.table.2),
    tab_spanner = c("**Post v. Pre**", "**Pathway v. No Pathway**")
  ) %>% as_gt()
table.2 
```

## Regression Outcomes

### Primary Outcome: *Advocate Contacted*

```{r advocate regression function}
advocate.regression<-function(data, exposure){
  data$advocate_offered <- as_factor(data$advocate_offered )
  data$advocate_offered <- relevel(data$advocate_offered, ref= "No Documentation of Pt Advocate")
  model <-  glm(advocate_offered ~ exposure + age + race_eth_num + ipv+ intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```

All patients

```{r regression1, echo=FALSE}
cohort.1 <- cohort.1 %>% mutate(exposure = if_else(pathway == "Used Pathway", 1, 0)) %>% set_variable_labels(sane_ED = "ED with SANE program", race_eth_num = "Race and Ethnicity", exposure = "Exposure", age = "Age", ipv = "Assailant was Intimate Partner", intoxicated= "Intoxicated")
pp.cohort.2 <- pp.cohort.2 %>% mutate(exposure = exposure.num) %>% set_variable_labels(sane_ED = "ED with SANE program", race_eth_num = "Race and Ethnicity", exposure = "Exposure", age = "Age", ipv = "Assailant was Intimate Partner", intoxicated= "Intoxicated")
pp.cohort.1 <- pp.cohort.1 %>% mutate(exposure = exposure.num) %>% set_variable_labels(sane_ED = "ED with SANE program", race_eth_num = "Race and Ethnicity", exposure = "Exposure", age = "Age", ipv = "Assailant was Intimate Partner", intoxicated= "Intoxicated")
tbl.reg.path.adv <-advocate.regression(cohort.1, cohort.1$exposure)
tbl.reg.pp.adv <-advocate.regression(pp.cohort.1, pp.cohort.1$exposure)
tbl.reg.prepn.adv <-advocate.regression(pp.cohort.2, pp.cohort.2$exposure)
tbl.all.adv <- tbl_merge(list(tbl.reg.pp.adv, tbl.reg.path.adv, tbl.reg.prepn.adv), tab_spanner = c("**Post v. Pre**", "**Pathway v. No Pathway**", "**No Pathway v. Pre**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate")
tbl.all.adv
```

### Primary Outcome: *SANE Kit*

note: restricted to pts \<120 hours from assault
no longer restricted to female (only 12 men) english speakers (only 11 non-english speaking)

```{r sane kit fxns, eval=FALSE, include=FALSE}
sane.off.reg<-function(data, exposure){
  model <-  logistf(sane_kit_offered ~ exposure + age + race_eth_num + ipv+ intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  model.results <- model.results %>% modify_header(estimate = "**OR**")
  return(model.results)
}
```

no longer including as outcome: Method: *2-Profile penalized log-likelihood*

SANE Kit Offered?

```{r}
pp.cohort.1.u120 <- pp.cohort.1 %>% filter(under120h == TRUE) %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
pp.cohort.1.u120$sane_kit_offered <- as_factor(pp.cohort.1.u120$sane_kit_offered)
pp.cohort.1.u120$sane_kit_offered <- relevel(pp.cohort.1.u120$sane_kit_offered, ref = "No")
pp.cohort.1.u120 <- pp.cohort.1 %>% filter(under120h == TRUE) %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
pp.cohort.1.u120$sane_kit_offered <- as_factor(pp.cohort.1.u120$sane_kit_offered)
pp.cohort.1.u120$sane_kit_offered <- relevel(pp.cohort.1.u120$sane_kit_offered, ref = "No")
pp.cohort.2.u120 <- pp.cohort.2 %>% filter(under120h == TRUE) %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
pp.cohort.2.u120$sane_kit_offered <- as_factor(pp.cohort.2.u120$sane_kit_offered)
pp.cohort.2.u120$sane_kit_offered <- relevel(pp.cohort.2.u120$sane_kit_offered, ref = "No")
path.u120 <- cohort.1 %>% filter(under120h == TRUE) %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
path.u120$sane_kit_offered <- as_factor(path.u120$sane_kit_offered)
path.u120$sane_kit_offered <- relevel(path.u120$sane_kit_offered, ref = "No")
```


```{r Sane kit offered regression, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
pp.cohort.1.u120 <- pp.cohort.1 %>% filter(under120h == TRUE) %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
pp.cohort.1.u120$sane_kit_offered <- as_factor(pp.cohort.1.u120$sane_kit_offered)
pp.cohort.1.u120$sane_kit_offered <- relevel(pp.cohort.1.u120$sane_kit_offered, ref = "No")
pp.cohort.2.u120 <- pp.cohort.2 %>% filter(under120h == TRUE) %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
pp.cohort.2.u120$sane_kit_offered <- as_factor(pp.cohort.2.u120$sane_kit_offered)
pp.cohort.2.u120$sane_kit_offered <- relevel(pp.cohort.2.u120$sane_kit_offered, ref = "No")
path.u120 <- cohort.1 %>% filter(under120h == TRUE) %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered"))
path.u120$sane_kit_offered <- as_factor(path.u120$sane_kit_offered)
path.u120$sane_kit_offered <- relevel(path.u120$sane_kit_offered, ref = "No")
pp.off.sk<-sane.off.reg(pp.cohort.1.u120, pp.cohort.1.u120$exposure)
path.off.sk<-sane.off.reg(path.u120, path.u120$exposure)
prenp.off.sk<-sane.off.reg(pp.cohort.2.u120, pp.cohort.2.u120$exposure) 
#_Likelihood ratio test=13.18587 on 8 df, p=0.1056123, n=383_

table.reg.offsk<- tbl_merge(list(pp.off.sk, path.off.sk, prenp.off.sk), tab_spanner = c("**Post v. Pre**", "**Pathway v. No Pathway**", "**No Pathway v. Pre**")) %>% as_gt() %>% tab_header("Odds of Offering SANE Kit if <120hr")
table.reg.offsk
```

SANE Kit Done?

```{r sane did fxn}
sane.did.reg<-function(data, exposure){
  model <-  glm(did_SANE_kit ~ exposure + age + race_eth_num + ipv+ intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```

```{r}
pp.cohort.1.u120 <- pp.cohort.1.u120 %>% mutate(did_SANE_kit = if_else(sane_kit_YN == "Yes", 1, 0))
pp.cohort.2.u120 <- pp.cohort.2.u120 %>% mutate(did_SANE_kit = if_else(sane_kit_YN == "Yes", 1, 0))
path.u120 <- path.u120 %>% mutate(did_SANE_kit = if_else(sane_kit_YN == "Yes", 1, 0))

pp.sk.did <- sane.did.reg(pp.cohort.1.u120, pp.cohort.1.u120$exposure)
prenp.sk.did <- sane.did.reg(pp.cohort.2.u120, pp.cohort.2.u120$exposure)
path.sk.did <-sane.did.reg(path.u120, path.u120$exposure)
table.reg.sk <- tbl_merge(list(pp.sk.did, path.sk.did, prenp.sk.did), tab_spanner = c("**Post v. Pre**", "**Pathway v. No Pathway**", "**No Pathway v. Pre**")) %>% as_gt() %>% tab_header("Odds of Doing SANE Kit if <120hrs")
table.reg.sk
```

### Secondary Outcome: *For Women =< 55 Presenting < 120 Hours*

```{r}
preg.test.reg<-function(data, exposure){
  model<-glm(pregnancy_test_ordered_num ~ exposure + age + race_eth_num + ipv+ intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}

preg.prev.reg<-function(data, exposure){
   model<-glm(prevent.preg ~ exposure + age + race_eth_num + ipv+ intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```

Pregnancy test ordered?

```{r preg test reg table}
preg.test.pp<-pp.cohort.1.u120 %>% filter(female == 1, age <= 55) %>% preg.test.reg(., .$exposure)
preg.test.prenp<-pp.cohort.2.u120 %>% filter(female == 1, age <= 55) %>% preg.test.reg(., .$exposure)
preg.test.path<-path.u120 %>% filter(female == 1, age <= 55) %>% preg.test.reg(., .$exposure)
table.reg.pregtest <- tbl_merge(list(preg.test.pp, preg.test.path, preg.test.prenp), tab_spanner = c("**Post v. Pre**", "**Pathway v. No Pathway**", "**No Pathway v. Pre**")) %>% as_gt() %>% tab_header("Odds of Pregnancy Test Ordered (if =/<55 & <120 hrs)")
table.reg.pregtest

```

Pregnancy prophylaxis ordered?

```{r preg pep table}
preg.prev.pp<-pp.cohort.1.u120 %>% filter(female == 1, age <= 55) %>% preg.prev.reg(., .$exposure)
preg.prev.prenp<-pp.cohort.2.u120 %>% filter(female == 1, age <= 55) %>% preg.prev.reg(., .$exposure)
preg.prev.path<-path.u120 %>% filter(female == 1, age <= 55) %>% preg.prev.reg(., .$exposure)
table.reg.pregprev <- tbl_merge(list(preg.prev.pp, preg.prev.path, preg.prev.prenp), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**", "**Pre v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of Pregnancy Prophylaxis Ordered (if =/<55 & <120 hrs)")
table.reg.pregprev
```

### Secondary Outcome: *HIV PEP*

```{r Hiv PEP fxn}
hiv.pep.reg<-function(data, exposure){
  model<-glm(hiv_pep_kit_ordered_num ~ exposure + age + race_eth_num + ipv + intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```

```{r HIV PEP table, message=FALSE, warning=FALSE}
pathway.u72 <- cohort.1 %>% filter(u72 == 1)
pp.u72 <- pp.cohort.1 %>% filter(u72 == 1)
prenp.u72 <- pp.cohort.2 %>% filter(u72 == 1)
tbl.pep.pp <- hiv.pep.reg(pp.u72, pp.u72$exposure)
tbl.pep.path <- hiv.pep.reg(pathway.u72, pathway.u72$exposure)
#### WARNING. Non-convirgence for no path vs pre. has to do with zero cell in ipv variable. does it matter?
tbl.pep.prenp <- hiv.pep.reg(prenp.u72, prenp.u72$exposure)
tbl.pep.hiv <- tbl_merge(list(tbl.pep.pp, tbl.pep.path, tbl.pep.prenp), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**", "**Pre v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of Receiving HIV PEP if Presented to ED <72 Hours Since Assault")
tbl.pep.hiv
```

### Secondary Outcome: *ABX given*

refers to any abx given, not looking at correct med/dosage

```{r abx given regression function}
abx.pep.reg<-function(data, exposure){
  model<-glm(abx_given ~ exposure + age + race_eth_num + ipv + intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```

```{r abx regression}
tbl.reg.path.abx <-abx.pep.reg(cohort.1, cohort.1$exposure)
tbl.reg.pp.abx <-abx.pep.reg(pp.cohort.1, pp.cohort.1$exposure)
tbl.reg.prepn.abx <-abx.pep.reg(pp.cohort.2, pp.cohort.2$exposure)
tbl.all.abx <- tbl_merge(list(tbl.reg.pp.abx, tbl.reg.path.abx, tbl.reg.prepn.abx), tab_spanner = c("**Post v. Pre**", "**Pathway v. No Pathway**", "**No Pathway v. Pre**")) %>% as_gt() %>% tab_header("Odds of Ordering Antibiotics")
tbl.all.abx
```

### Tertiary Outcome: *Follow Up at Discharge?*

note: removed outcome on 8/22/24
```{r follow up regression function, eval=FALSE, include=FALSE}
fu.reg<-function(data, exposure){
  model<-glm(follow_up_at_discharge ~ exposure + age + race_eth_num + ipv + intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```

```{r fu regression, eval=FALSE, include=FALSE}
tbl.reg.path.fu <-fu.reg(cohort.1, cohort.1$exposure)
tbl.reg.pp.fu <-fu.reg(pp.cohort.1, pp.cohort.1$exposure)
tbl.reg.prepn.fu <-fu.reg(pp.cohort.2, pp.cohort.2$exposure)
tbl.all.fu <- tbl_merge(list(tbl.reg.pp.fu, tbl.reg.path.fu, tbl.reg.prepn.fu), tab_spanner = c("**Post v. Pre**", "**Pathway v. No Pathway**", "**No Pathway v. Pre**")) %>% as_gt() %>% tab_header("Odds of Having Follow Up at Discharge")
tbl.all.fu
```

### Restricted to YSC and SRC

```{r}
#create cohort restricted to YSC and SRC (SAFE program sites)

SAFE_Site_Cohort <- pp.cohort.1 %>% 
  filter(sane_ED == 1)
SAFE_Site_Cohort_u120 <- SAFE_Site_Cohort %>% 
   mutate(did_SANE_kit = if_else(sane_kit_YN == "Yes", 1, 0)) %>%
  filter(under120h == TRUE) #383 patients u120 at SAFE sites
SAFE_Site_Cohort_u120.f <- SAFE_Site_Cohort_u120 %>% filter(female_u55 == 1)
SAFE_Site_Cohort_u72 <- SAFE_Site_Cohort %>% filter(u72 == 1)
# number of patients who had pathway used
SAFE_Site_Cohort %>% filter(agile_md_used_num == 1) %>% nrow() %>% print()
SAFE_Site_Cohort_u120 %>% filter(agile_md_used_num == 1) %>% nrow() %>% print()

# SAFE Kit Done; restricted to u120
reg.ss.sk.did <-  glm(did_SANE_kit ~ exposure + age + race_eth_num + ipv+ intoxicated, family = "binomial", data = SAFE_Site_Cohort_u120)
tbl.reg.ss.sk.did <- tbl_regression(reg.ss.sk.did, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Odds of Doing SAFE Kit (Restricted to YSC/SRC)")
tbl.reg.ss.sk.did
# advocate offered

  SAFE_Site_Cohort$advocate_offered <- as_factor(SAFE_Site_Cohort$advocate_offered )
  SAFE_Site_Cohort$advocate_offered <- relevel(SAFE_Site_Cohort$advocate_offered, ref= "No Documentation of Pt Advocate")
  reg.ss.adv <-  glm(advocate_offered ~ exposure + age + race_eth_num + ipv+ intoxicated, family = "binomial", data = SAFE_Site_Cohort)
  tbl.reg.ss.adv <- tbl_regression(reg.ss.adv, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Odds of Offering Advocate (Restricted to YSC/SRC)")
  tbl.reg.ss.adv

# pregnancy test ordered
   reg.ss.preg <-glm(pregnancy_test_ordered_num ~ exposure + age + race_eth_num + ipv+ intoxicated, family = "binomial", data = SAFE_Site_Cohort_u120.f)
  tbl.reg.ss.preg <- tbl_regression(reg.ss.preg, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Odds of Ordering Pregnancy Test (Restricted to YSC/SRC)")
  tbl.reg.ss.preg
# EC ordered
  reg.ss.ec<-glm(prevent.preg ~ exposure + age + race_eth_num + ipv+ intoxicated, family = "binomial", data = SAFE_Site_Cohort_u120.f)
  tbl.reg.ss.ec <- tbl_regression(reg.ss.ec, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Odds of Ordering Emergency Contraception (Restricted to YSC/SRC)")
  tbl.reg.ss.ec
# HIV Prophylaxis ordered
  reg.ss.hiv <-glm(hiv_pep_kit_ordered_num ~ exposure + age + race_eth_num + ipv + intoxicated, family = "binomial", data = SAFE_Site_Cohort_u72)
  tbl.reg.ss.hiv <- tbl_regression(reg.ss.hiv, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Odds of Ordering HIV PEP (Restricted to YSC/SRC)")
  tbl.reg.ss.hiv
# Abx ordered
   reg.ss.abx <-glm(abx_given ~ exposure + age + race_eth_num + ipv + intoxicated, family = "binomial", data = SAFE_Site_Cohort)
  tbl.reg.ss.abx <- tbl_regression(reg.ss.abx, exponentiate = TRUE) %>% add_global_p() %>% as_gt() %>% tab_header("Odds of Ordering Antibiotics (Restricted to YSC/SRC)")
  tbl.reg.ss.abx
```


## Graphs

### Updated CI Graph

```{r updated CI graph}
OR_Data<- read_excel("~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/OR_Table_Data.xlsx") %>% mutate(lnOR = log(OR), lnLCI = log(LCI), lnUCI=log(UCI))
OR_Data <- OR_Data %>%  mutate(Measure = fct_relevel(Measure, "Antibiotics Ordered", "HIV Prophylaxis Ordered", "Emergency Contraception Ordered", "Pregnancy Test Ordered","SAFE Kit Done", "Advocate Offerred" )) 
FinalArrowMsg = "Less likely                        OR                        More likely"
TitleStr <-  paste("Association Between", sep = " ", collapse = NULL)
TitleStr <- paste(TitleStr,'Exposure and ED Outcome Measures', sep = " ", collapse = NULL)
pd <- position_dodge(width = 0.6)
  p <- ggplot(OR_Data, aes(OR, Measure, group = Exposure))
  CI_Log_Graph <- p + geom_point(position = pd, aes(shape=Exposure, color=Exposure)) + geom_errorbarh(aes(xmax = UCI, xmin = LCI, color = Exposure),height = 0.2,position = pd) + labs(x =FinalArrowMsg, y = "ED Outcome Measures",color = "Exposure", shape= "Exposure")+
    theme(
      plot.title = element_text(size=15),
      axis.title.x = element_text(size=13),
      axis.title.y = element_text(size=14),
      plot.caption = element_text(hjust = 0, face= "italic",size=10),
      axis.line.x = element_line(arrow = grid::arrow(length = unit(0.3, "cm"),ends = "both")),
      axis.text.y = element_text(size=12),
      axis.text.x = element_text(size=10),
      legend.text=element_text(size=12),
      legend.title = element_text(size = 14),
      legend.key.height=unit(1, "cm")
    ) +  
    geom_vline(xintercept = 1)  + 
    scale_x_log10() + 
    labs(caption = "Note: Horizontal lines are 95% confidence intervals")+
    ggtitle(TitleStr) + theme(plot.title = element_text(hjust = 0.5))+
    guides(color = guide_legend(reverse=TRUE),shape =guide_legend(reverse=TRUE))
CI_Log_Graph
CI_Log_Graph + scale_x_log10(limits = c(0.05, 25), n.breaks = 6)
  CI_Graph <- p + geom_point(position = pd,aes(shape=Exposure, color=Exposure)) + geom_errorbarh(aes(xmax = UCI, xmin = LCI, color = Exposure),height = 0.1,position = pd) + labs(x =FinalArrowMsg, y = "ED Outcome Measures",color = "Exposure", shape= "Exposure")+
    theme(
      plot.title = element_text(size=15),
      axis.title.x = element_text(size=12, vjust = -.05),
      axis.title.y = element_text(size=14),
      plot.caption = element_text(hjust = 0, face= "italic",size=10),
      axis.line.x = element_line(arrow = grid::arrow(length = unit(0.3, "cm"),ends = "both")),
      axis.text.y = element_text(size=12),
      axis.text.x = element_text(size=11),
      legend.text=element_text(size=12),
      legend.title = element_text(size = 14),
      legend.key.height=unit(1, "cm")
    ) +  
    geom_vline(xintercept = 1)  + 
    labs(caption = "Note: Horizontal lines are 95% confidence intervals")+
    ggtitle(TitleStr) + theme(plot.title = element_text(hjust = 0.5)) +
    guides(color = guide_legend(reverse=TRUE),shape =guide_legend(reverse=TRUE))

CI_Graph
```

CI Graph for Post V. Pre for SAFE Sites (defined as YSC or SRC discharge)

```{r CI graph SAFE SITES}
SAFE_SITE_OR_Data <- read_excel("~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/SAFE_SITE_OR_Data.xlsx")

ggplot(SAFE_SITE_OR_Data, aes(OR, Measure)) + geom_errorbar(aes(xmax = UCI, xmin = LCI), color = "blue", height = 0.1) + geom_vline(xintercept = 1) + geom_point(shape = "square") + scale_x_log10() + ggtitle("CI Graph for Post V. Pre for SAFE Sites")+ scale_x_log10(limits = c(0.05, 25), n.breaks = 6)

```


### Percent pathway, sane kit done and advocate offered over time

```{r line over time graphs}
month_line_df <-
  pp.cohort.1 %>% mutate(
    month = ceiling_date(arrive_dt, unit = "month"),
    advocate = case_when(
      advocate_offered == "Advocate Offered" ~ 1,
      advocate_offered == "No Documentation of Pt Advocate" ~ 0,
      .default = NA
    ),
    did_SANE_kit = case_when(
      under120h == TRUE & sane_kit_done == 1 ~ 1,
      under120h == TRUE & sane_kit_done != 1 ~ 0,
      .default = NA
    ),
  ) %>%
  group_by(month) %>% summarise(
    Percent_Advocate = mean(advocate),
    Percent_Pathway = mean(agile_md_used_num, na.rm = FALSE),
    Percent_Sane = mean(did_SANE_kit, na.rm = TRUE)
  ) %>% gather(key = "Metric", value = "Percent", -month) %>% filter(Percent !=0) %>% mutate(Metric = factor(Metric, labels = c("Percent_Advocate" = "% Advocate",  "Percent_Pathway" = "% Pathway", "Percent_Sane" = "% SAFE Kit")))

month_line_df %>% ggplot(aes(x = month, y = Percent, color = Metric)) + geom_point() + geom_path() + scale_y_continuous(labels = scales::percent) + geom_vline(xintercept = pathway_start, color = "black", linetype= 'longdash') + geom_vline(xintercept = sb_start, color= "darkgrey", linetype= 'longdash') + theme_minimal()

quarter_line_df <-
  pp.cohort.1 %>% mutate(
    quarter = ceiling_date(arrive_dt, unit = "quarter"),
    advocate = case_when(
      advocate_offered == "Advocate Offered" ~ 1,
      advocate_offered == "No Documentation of Pt Advocate" ~ 0,
      .default = NA
    ),
    did_SANE_kit = case_when(
      under120h == TRUE & sane_kit_done == 1 ~ 1,
      under120h == TRUE & sane_kit_done != 1 ~ 0,
      .default = NA
    )) %>%
  group_by(quarter) %>% summarise(
    Percent_Advocate = mean(advocate),
    Percent_Pathway = mean(agile_md_used_num),
    Percent_Sane = mean(did_SANE_kit, na.rm = TRUE)
  ) %>% gather(key = "Metric", value = "Percent", -quarter) %>% filter(Percent !=0) %>% mutate(Metric = factor(Metric, labels = c("Percent_Advocate" = "% Advocate",  "Percent_Pathway" = "% Pathway", "Percent_Sane" = "% SAFE Kit")))


quarter_percent_plot<- quarter_line_df %>% ggplot(aes(x = quarter, y = Percent, color = Metric)) + geom_point() + geom_path() + theme_minimal() + scale_fill_brewer(palette = "Set1") + scale_y_continuous(labels = scales::percent, limits=c(0,1)) + geom_vline(xintercept = pathway_start, color = "black", linetype= 'longdash') + geom_vline(xintercept = sb_start, color= "darkgrey", linetype= 'longdash')
quarter_percent_plot + xlab("Quarter")
```

### Percent pathway utilization over time

```{r visits-over-time-month}
time_graph_1 <- all_pts %>% mutate(month = ceiling_date(arrive_dt, "month")) %>% ggplot() + geom_bar(mapping = aes(x = month, fill = pathway)) + theme_minimal() + scale_fill_brewer(palette = "Set1") + labs(title = "Patients Per Month", y = "Number of Visits", x= "Month", fill = NULL) + geom_vline(xintercept = pathway_start, color = "black", linetype= 'longdash', alpha = 0.7)
time_graph_1
```

```{r visits-over-time-quarter}
time_graph_2 <- all_pts %>% mutate(quarter = ceiling_date(arrive_dt, "quarter")) %>% ggplot() + geom_bar(mapping = aes(x = quarter, fill = pathway)) + theme_minimal() + scale_fill_brewer(palette = "Set1") + labs(title = "Patients Per Quarter", y = "Number of Visits", x= "Quarter", fill = NULL) + geom_vline(xintercept = pathway_start, color = "black", linetype= 'longdash', alpha = 0.7)
time_graph_2
```


```{r alternative-visits-pathway-time graphs, eval=FALSE, include=FALSE}
ppm <- all_pts %>% mutate(month = floor_date(arrive_dt, "month")) %>% group_by(month) %>% summarise(n = n(), pathway = sum(agile_md_used_num), percent.path = 100*(sum(agile_md_used_num)/n())) %>% mutate(no_pathway = n - pathway) %>% select(-n) %>%  gather(key = "visit_type", value = "visits", -month, -percent.path)
ppm %>% ggplot() + geom_col(aes(x = month, y = visits, fill = visit_type)) + geom_borderline(aes(x = month, y = percent.path), color = "#377EB8", bordercolour = "grey", borderwidth = 0.25) + labs(title = "Patients per month", y = "Number of visits", x= "Month", fill = "Pathway") + theme_minimal() + scale_fill_brewer(palette = "Set1") + scale_y_continuous(sec.axis=sec_axis(~.*0.01, name="Percent of Visits with Pathway Used", labels=scales::percent))
ppq <- all_pts %>% mutate(quarter = floor_date(arrive_dt, "quarter")) %>% group_by(quarter) %>% summarise(n = n(), pathway = sum(agile_md_used_num), percent.path = 100*(sum(agile_md_used_num)/n())) %>% mutate(no_pathway = n - pathway) %>% select(-n) %>%  gather(key = "visit_type", value = "visits", -quarter, -percent.path)
ppq %>% ggplot() + geom_col(aes(x = quarter, y = visits, fill = visit_type)) + geom_borderline(aes(x = quarter, y = percent.path), color = "#377EB8", bordercolour = "grey", borderwidth = 0.25) + labs(title = "Patients per quarter", y = "Number of visits", x= "quarter", fill = "Pathway") + theme_minimal() + scale_fill_brewer(palette = "Set1") + scale_y_continuous(sec.axis=sec_axis(~.*0.01, name="Percent of Visits with Pathway Used", labels=scales::percent))
```

### OR Graph
no longer using
```{r alt-or-graphs, eval=FALSE, include=FALSE}

CI_Plot <- ggplot(OR_Data, aes(x = factor(Exposure), y = OR, color = factor(Exposure))) + geom_errorbar(aes(ymin =`LCI`, ymax = `UCI`), position = "dodge") + facet_wrap(vars(Measure)) + geom_hline (yintercept = 1, linetype = "dashed")
CI_Plot + theme_light() + guides(color = "none") + coord_flip() + labs (x = "Exposure")

lnCI_Plot <- ggplot(OR_Data, aes(x = factor(Exposure), y = lnOR, color = factor(Exposure))) + geom_errorbar(aes(ymin =`lnLCI`, ymax = `lnUCI`), position = "dodge") + facet_wrap(vars(Measure), labeller = labeller(Measure = label_wrap_gen(50))) + geom_hline (yintercept = 0, linetype = "dashed") + labs (x = "Exposure")
lnCI_Plot + guides(color = "none") + theme_light() + theme(axis.text.x = element_text(angle = 90), axis.title.x = element_blank()) + coord_flip()
```
