---
title: "SA Paper 1 Analysis"
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
---
## Prep Code
```{r Initial Data and Package Prep, message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(logistf)
library(tidyverse)
library(lubridate)
library(gtsummary)
library(gt)
library(parsedate)
library(janitor)
library(labelled)
library(parameters)
library(survival)
library(ggsurvfit)
library(table1)
library(hms)
library(readxl)
library(ggborderline)
epicdata <-
  read_excel(
    "~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/C_F_AllPatients_2020to2023.xlsx"
  ) %>% select(1, contains("Location")) %>% rename("pat_enc_csn_id" = "Pat Enc Csn ID...1") %>% clean_names()
all_pts <-
  read_csv(
    "~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/SA_pts_reformatted.csv"
  )
all_pts <- left_join(all_pts, epicdata, by = "pat_enc_csn_id")
# updates pts with erroneous NAs in reason to exclude. Manually coded by DY 2/29/2024 and sent as CSV. 
u_reason_exclude <- read_csv("~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/Why_Excluded")
update_pts_CSN<-u_reason_exclude$pat_enc_csn_id
u_reason_exclude <- u_reason_exclude %>% select(pat_enc_csn_id, reason_to_exclude)
# replaces erroneous NAs for 15 patients
all_pts <- left_join(all_pts, u_reason_exclude, suffix = c(".x", ".y"))
# set TZ to east coast standard
time_zone <- "America/New_York"
#pathway went live on 7/13/21
pathway_start <- mdy("7/13/21", tz = time_zone)
#Story board notification went live on 9/8/21
sb_start <- mdy("9/8/21", tz = time_zone)
day.arrival.start <- hms::as_hms("03:00:00")
night.arrival.start <- hms::as_hms("15:00:00")
# making outcome variable for if correct STI tx: CTX, azithromycin or doxy (and flagyl if female) are ordered
all_pts <- all_pts %>% mutate(
  azithro_or_doxy = case_when(
    azithromycin_ordered_num | doxycycline_ordered_num == 1 ~ 1,
    azithromycin_ordered_num == 0 &
      doxycycline_ordered_num == 0 ~ 0,
    .default = 0
  )
) %>% mutate(
  sti_tx = case_when(
    gender == "Male" &
      ceftriaxone_ordered_num == 1 & azithro_or_doxy == 1 ~ 1,
    gender == "Male" &
      ceftriaxone_ordered_num | azithro_or_doxy == 0  ~ 0,
    gender == "Female" &
      ceftriaxone_ordered_num == 1 &
      azithro_or_doxy == 1 &
      flagyl_or_metronidazole_ordered_num == 1 ~ 1,
    gender == "Female" &
      ceftriaxone_ordered_num |
      azithro_or_doxy |
      flagyl_or_metronidazole_ordered_num == 0 ~ 0,
    .default = 0
  ),
  chem_ordered = case_when(
    cmp_ordered_yn == "Y" | bmp_ordered_yn == "Y" ~ 1,
    cmp_ordered_yn == "N" & bmp_ordered_yn == "N" ~ 0,
    .default = NA
  ),
  abx_given = case_when(
    ceftriaxone_ordered_num == 0 &
      azithro_or_doxy == 0 &
      flagyl_or_metronidazole_ordered_num == 0 ~ 0,
    ceftriaxone_ordered_num == 1 |
      azithro_or_doxy == 1 |
      flagyl_or_metronidazole_ordered_num == 1 ~ 1
  ),
  lfts_ordered = case_when(
    cmp_ordered_yn == "Y" | lft_ordered_yn == "Y" ~ 1,
    cmp_ordered_yn == "N" & lft_ordered_yn == "N" ~ 0,
    .default = NA
  )
) %>% mutate(
  hiv_labs = case_when(
    hiv_pep_kit_ordered_num == 1 &
      chem_ordered == 1 & lfts_ordered == 1 ~ 1,
    hiv_pep_kit_ordered_num == 1 &
      (chem_ordered == 0 | lfts_ordered == 0) ~ 0,
    .default = 0
  ),
  prevent.preg = case_when(
    plan_b_or_levonorgestrel_ordered_num == 1 |
      ulipristal_ordered_num == 1 ~ 1,
    plan_b_or_levonorgestrel_ordered_num == 0 &
      ulipristal_ordered_num == 0 ~ 0,
    .default = NA
  ),
  advocate_offered = case_when(
    patient_advocate_called == 1 |
      patient_advocate_called == 3 ~ "Advocate Offered",
    patient_advocate_called == 0 |
      patient_advocate_called == 2 ~ "No Documentation of Pt Advocate",
    .default = NA
  ),
  sane_kit_YN = case_when(
    sane_kit_done == 0 ~ "No",
    sane_kit_done == 1 ~ "Yes",
    sane_kit_done == 2 ~ "Offered, but declined",
    sane_kit_done == 3 ~ "Outside 120 hr Window",
    sane_kit_done == 4 ~ "Not done due to concurrent psychiatric concerns"
  ),
  sane_kit_missed = case_when(
    sane_kit_done == 0 ~ "SANE kit not done/documented",
    sane_kit_done %in% c(1, 2, 3) ~ "SANE kit done/not indicated",
    sane_kit_done == 4 ~ "Not done due to concurrent psychiatric concerns"
  ),
  sane_kit_offered = case_when(
    sane_kit_done == 1 | sane_kit_done == 2  ~ "Sane Kit Offered",
    sane_kit_done == 0 |
      sane_kit_done == 3 | sane_kit_done == 4 ~ "Sane Kit Not Offered"
  ),
  sane_ED = if_else(discharge_location %in% c("YSC", "YSC-CIU", "SRC"), 1, 0),
  pathway = if_else(
    date(arrive_dt) < date(pathway_start),
    "Didn't Use Pathway",
    pathway
  ),
  agile_md_used_num = if_else(date(arrive_dt) < date(pathway_start), 0 , agile_md_used_num)
) %>%
  mutate(
    tbl_sti_tx = case_when(
      sti_tx == 1 & abx_given == 1 ~ 1,
      sti_tx == 0 & abx_given == 1 ~ 0,
      .default = NA
    ),
    tbl_prevent_hiv = case_when(
      time_since_sexual_assault_if_number_k_is_y != 0 ~ NA,
      time_since_sexual_assault_if_number_k_is_y == 0 &
        hiv_pep_kit_ordered_num == 1 ~ 1,
      time_since_sexual_assault_if_number_k_is_y == 0 &
        hiv_pep_kit_ordered_num == 0 ~ 0
    ),
    tbl_hiv_labs = case_when(
      hiv_pep_kit_ordered_num == 1 & hiv_labs == 1 ~ 1,
      hiv_pep_kit_ordered_num == 1 & hiv_labs == 0 ~ 0,
      .default = NA
    ),
    tbl_preg_test = case_when(
      female_u55 == 1 & pregnancy_test_ordered_num == 1 ~ 1,
      female_u55 == 1 & pregnancy_test_ordered_num == 0 ~ 0,
      .default = NA
    ),
    tbl_prevent_preg = case_when(
      female_u55 == 1 & prevent.preg == 1 ~ 1,
      female_u55 == 1 & prevent.preg == 0 ~ 0,
      .default = NA
    ),
    under120h = case_when(
      time_since_sexual_assault_if_number_k_is_y == 0 |
        time_since_sexual_assault_if_number_k_is_y == 1 ~ TRUE,
      time_since_sexual_assault_if_number_k_is_y == 2 |
        time_since_sexual_assault_if_number_k_is_y == 3 ~ FALSE,
      .default = NA
    ),
    u72 = if_else(time_since_sexual_assault_if_number_k_is_y == 0, 1, 0),
    english = case_when(
      patient_language == "English" ~ 1,
      is.na(patient_language) ~ NA,
      .default = 0
    ),
    ambulance = if_else(method_of_arrival == 1, 1, 0),
    relationship_with_patient = factor(
      relationship_with_patient,
      levels = c(0, 1, 2, 3, 4, NA),
      labels = c(
        "Unknown",
        "Aqauintance",
        "Family member",
        "Stranger",
        "Intimate Partner",
        NA
      ),
      exclude = NULL,
      ordered = FALSE
    ),
    insurance_3 = case_when(
      insurance == "Private Insurance" ~ "Private",
      insurance %in% c("Medicaid", "Medicare", "Sexual Assault") ~ "Public",
      insurance == "Uninsured/Self-Pay" ~ "Uninsured"
    ),
    SA_insurance = if_else(insurance == "Sexual Assault", 1, 0)
  ) %>%
  mutate(
    relationship_4_with_pt = case_when(
      relationship_with_patient == "Family member" ~ "Family",
      relationship_with_patient == "Aqauintance" ~ "Aquaintaince",
      relationship_with_patient == "Intimate Partner" ~ "Intimate Partner",
      relationship_with_patient == "Unknown" |
        relationship_with_patient == "Stranger" ~ "Stranger/Unknown"
    ),
    intoxicated = case_when(Etoh == 1 | Drugs == 1 ~ 1,
                            Etoh == 0 & Drugs == 0 ~ 0,
                            .default = 0),
    sane_advocate_offered = if_else(
      advocate_offered == "Advocate Offered" &
        sane_kit_offered == "Sane Kit Offered",
      1,
      0
    ),
    ipv = if_else(relationship_with_patient == "Intimate Partner", 1, 0)
  ) %>%
  mutate(arrive_time = as_hms(arrive_dt)) %>%
  mutate(
    day_night = case_when(
      arrive_time >= day.arrival.start &
        arrive_time <= night.arrival.start ~ "Day",
      arrive_time < day.arrival.start |
        arrive_time > night.arrival.start ~ "Night",
      .default = "ERROR"
    )
  ) %>%
  mutate(threeto3 = if_else(day_night == "Day", 1, 0)) %>%  #adding line to make it so patients who did not have sane kit done due to psych concerns are excluded
  mutate(exclude = case_when(
    exclude == 1 ~ 1,
    sane_kit_done == 4 ~ 1,
    is.na(exclude) ~ NA,
    .default = NA
  ))
all_pts$insurance_3 <- as_factor(all_pts$insurance_3)
all_pts$insurance_3 <- relevel(all_pts$insurance_3, ref = "Public")

number_of_minors <-
  all_pts %>% filter(age < 18) #changed it so age is first exclusion criteria
number_of_minors <-
  n_distinct(number_of_minors$pat_enc_csn_id, na.rm = TRUE) %>% as.character()
cat("  ", number_of_minors, "patients under 18 YO excluded")
excluded_patients <-
  all_pts %>% filter(age > 17) %>%  
  filter(exclude == 1) %>% mutate(reason_to_exclude = if_else(sane_kit_done == 4, 3, reason_to_exclude)) #if sane kit not done b/c psych that is also reason to eclude now
pp.cohort.1 <-
  all_pts %>% filter(between == 0) %>% filter(age > 17) %>% filter(is.na(exclude), sane_kit_done != 4) %>% mutate(exposure.tab = exposure.char)
excluded_patients <-
  excluded_patients %>% add_value_labels(
    reason_to_exclude = c(
      "Seen earlier" = 1 ,
      "Patient reports not being assaulted" = 2,
      "Psych" = 3,
      "not excluded" = 4,
      "Eloped" = 5
    )
  ) %>% to_factor()
excluded_patients %>% group_by(reason_to_exclude) %>% summarise(n = n()) %>% print()
between_pts <-
  all_pts %>% filter(age > 17, between == 1, is.na(exclude), sane_kit_done != 4)
n_between <-
  n_distinct(between_pts$pat_enc_csn_id, na.rm = TRUE) %>% as.character()
n_excluded <-
  n_distinct(excluded_patients$pat_enc_csn_id, na.rm = TRUE) %>% as.character()
cat("-", n_excluded, "patients were excluded based on chart review.")
cat(" ",
    n_between,
    "patients who arrived between 7/13/21 and 9/8/21 were excluded")
rm(n_excluded, number_of_minors, n_between)
cohort.1 <-
  all_pts %>% filter(ed_arrival_date > sb_start) %>% filter(age > 17) %>% filter(is.na(exclude)) %>% mutate(exposure.tab = pathway)

```

942 patient encounters from 2019-12-31 to 2022-12-24  
In order of exclusion: age -> chart review -> between period
<!-- 76 patients who arrived between 7/13/21 and 9/8/21 were excluded   -->
<!-- 247 patients under 18 YO excluded   -->
<!-- 36 patients were excluded based on chart review (13 seen earlier, 13 reported not actually being assaulted, 2 were purely psychiatric presentations, 8 eloped before evaluation could be completed)  -->

## Table 1 and 2
```{r tbl 1 fxn, echo=FALSE, message=FALSE, warning=FALSE}
tbl.one.fxn <- function(df) {
  x <- df %>% select(exposure.tab,
                     age,
                     female,
                     race_bwo,
                     under120h,
                     u72,
                     english,
                     ambulance,
                     intoxicated,
                     Psych,
                     ipv) %>%
    set_variable_labels(
      age = "Age",
      female = "Female",
      race_bwo = "Race",
      under120h = "Presented within 120h of assault",
      u72 = "Presented within 72h of assault",
      ambulance = "Arrived by EMS",
      english = "English speaking",
      ipv = "Assailant was Intimate Partner",
      intoxicated = "Diagnosis of Intoxication",
      Psych = "Psychiatric Diagnosis"
    ) %>%
    tbl_summary(
      by = exposure.tab,
      missing = "ifany",
      percent = "column",
      statistic = (age ~ "{median} ({p25}, {p75})")
    ) %>%
    add_p() %>% separate_p_footnotes()
  return(x)
}
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
pp.cohort.1$exposure.tab <- factor(pp.cohort.1$exposure.tab, levels=c("Pre-intervention", "Post-intervention"))
pp.table.1 <- tbl.one.fxn(pp.cohort.1) %>% add_overall()
table.1 <- tbl.one.fxn(cohort.1)
  table1 <-
    tbl_merge(
      list(pp.table.1, table.1),
      tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")
    ) %>% as_gt()
table1
```

```{r tbl 2 fxns, echo=FALSE, message=FALSE, warning=FALSE}
#note to self-> make it so males, over55 are NA so table can be fixed for proper %
tbl.two.fxn <- function(data) {
  x <- data %>% mutate(
    tbl_sane_kit_u120 = case_when(
      under120h == TRUE & sane_kit_done == 1 ~ 1,
      under120h == TRUE & sane_kit_done != 1 ~ 0,
      .default = NA
    ),
  ) %>%
    select(
      exposure.tab,
      advocate_offered,
      abx_given,
      tbl_prevent_hiv,
      female_u55,
      tbl_preg_test,
      tbl_prevent_preg,
      sane_ED,
      sane_kit_YN,
      tbl_sane_kit_u120,
      follow_up_at_discharge
    ) %>%
    set_variable_labels(
      advocate_offered = "Documentation of advocate contacted",
      abx_given = "PEP antibiotics ordered",
      tbl_prevent_hiv = "HIV PEP ordered (if < 72h from assault",
      female_u55 = "Female under 55",
      tbl_preg_test = "Pregnancy test ordered",
      tbl_prevent_preg = "Pregnancy prophalaxis ordered",
      sane_ED = "ED with SANE program",
      sane_kit_YN = "SANE kit done",
      tbl_sane_kit_u120 = "Under 120 hours and SANE kit done",
      follow_up_at_discharge = "Has after discharge follow up"
    ) %>% tbl_summary(
      by = exposure.tab,
      percent = "column",
      missing = "no",
      statistic = contains("tbl") ~ "{n}/{N_nonmiss} ({p}%)"
    ) %>% add_p() %>% separate_p_footnotes()
  return(x)
}

```


```{r tables, echo=FALSE, message=FALSE, warning=FALSE}
pp.cohort.1$exposure.tab <- factor(pp.cohort.1$exposure.tab, levels=c("Pre-intervention", "Post-intervention"))
pp.table.2 <-tbl.two.fxn(pp.cohort.1) %>% add_overall()
path.table.2 <-tbl.two.fxn(cohort.1)
 table.2 <-tbl_merge(
    list(pp.table.2, path.table.2),
    tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")
  ) %>% as_gt()
table.2 
```

## Regression Outcomes

### Primary Outcome: _Advocate Contacted_
removes patients who did not have sane kit done due to psych concerns
```{r advocate regression function}
advocate.regression<-function(data, exposure){
  data <- data %>% filter(sane_kit_done != 4)
  data$advocate_offered <- as_factor(data$advocate_offered )
  data$advocate_offered <- relevel(data$advocate_offered, ref= "No Documentation of Pt Advocate")
  model <-  glm(advocate_offered ~ exposure + age + female + white + english + ipv + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```


All patients
```{r regression1, echo=FALSE}
cohort.1 <- cohort.1 %>% mutate(exposure = if_else(pathway == "Used Pathway", 1, 0)) %>% set_variable_labels(sane_ED = "ED with SANE program")
pp.cohort.1 <- pp.cohort.1 %>% mutate(exposure = exposure.num) %>% set_variable_labels(sane_ED = "ED with SANE program")
tbl.reg.path.adv <-advocate.regression(cohort.1, cohort.1$exposure)
tbl.reg.pp.adv <-advocate.regression(pp.cohort.1, pp.cohort.1$exposure)

tbl.all.adv <- tbl_merge(list(tbl.reg.pp.adv, tbl.reg.path.adv), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate")
tbl.all.adv
```

Patients Under 120 Hours:

```{r under 120 regression, echo=FALSE}
pathway.u120 <- cohort.1 %>% filter(under120h == TRUE)
pp.u120 <- pp.cohort.1 %>% filter(under120h == TRUE)
tbl.reg.pp.adv.u120 <- advocate.regression(pp.u120, pp.u120$exposure)
tbl.reg.path.adv.u120 <- advocate.regression(pathway.u120, pathway.u120$exposure)
tbl.reg.adv.u120 <- tbl_merge(list(tbl.reg.pp.adv.u120, tbl.reg.path.adv.u120), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate if Presented to ED <120 Hours Since Assault")
tbl.reg.adv.u120
```
### Primary Outcome: _SANE Kit_
note: restricted to pts <120 hours from assault, female (only 12 men) english speakers (only 11 non-english speaking)
excludes patients who didn't have sane kit done for psych concerns
Peanlized LR
```{r sane kit fxns}
sane.off.reg<-function(data, exposure){
  model <-  logistf(sane_kit_offered ~ exposure + age + white + ipv + intoxicated + sane_ED, data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) 
  model.results <- model.results %>% modify_header(estimate = "**OR**")
  return(model.results)
}
```

SANE Kit Offered?
```{r}
fe.pp.u120 <-pp.u120 %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered")) %>%  filter(female == 1 & english ==1)
fe.pp.u120$sane_kit_offered <- as_factor(fe.pp.u120$sane_kit_offered)
fe.pp.u120$sane_kit_offered <- relevel(fe.pp.u120$sane_kit_offered, ref = "No")
fe.path.u120<- pathway.u120 %>% mutate(sane_kit_offered = if_else(sane_kit_done == 0, "No", "Offered")) %>%  filter(female == 1 & english ==1)
fe.path.u120$sane_kit_offered <- as_factor(fe.path.u120$sane_kit_offered)
fe.path.u120$sane_kit_offered <- relevel(fe.path.u120$sane_kit_offered, ref = "No")
pp.off.sk<-sane.off.reg(fe.pp.u120, fe.pp.u120$exposure)
path.off.sk<-sane.off.reg(fe.path.u120, fe.path.u120$exposure)
table.reg.offsk<- tbl_merge(list(pp.off.sk, path.off.sk), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of Offering SANE Kit if <120hr")
table.reg.offsk
```

SANE Kit Done?

```{r sane did fxn}
sane.did.reg<-function(data, exposure){
  data <- data %>% filter(sane_kit_done != 4)
  model <-  glm(did_SANE_kit ~ exposure + age + white + ipv + intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```

```{r}
fe.pp.u120 <- fe.pp.u120 %>% mutate(did_SANE_kit = if_else(sane_kit_YN == "Yes", 1, 0))
fe.path.u120<- fe.path.u120 %>% mutate(did_SANE_kit = if_else(sane_kit_YN == "Yes", 1, 0))
pp.sk.did <- sane.did.reg(fe.pp.u120, fe.pp.u120$exposure)
path.sk.did <-sane.did.reg(fe.path.u120, fe.path.u120$exposure)
table.reg.sk <- tbl_merge(list(pp.sk.did, path.sk.did), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of Doing SANE Kit if <120hrs")
table.reg.sk
```

### Secondary Outcome: _Advocate Contacted/Offerred *IF* SANE Kit Done (restricted to English speaking female patients)_

```{r english female only reg adv fxn} 
#makes regression but w/o female variable
f.advocate.regression<-function(data, exposure){
  data <- data %>% filter(sane_kit_done != 4)
  data$advocate_offered <- as_factor(data$advocate_offered)
  data$advocate_offered <- relevel(data$advocate_offered, ref= "No Documentation of Pt Advocate")
  model <-  glm(advocate_offered ~ exposure+ age + white + ipv +  intoxicated + sane_ED, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```


```{r under 120 SK done Reg, echo=FALSE}
pathway.u120.sk <- cohort.1 %>% filter(under120h == TRUE, sane_kit_YN == "Yes", female == 1, english == 1)
pp.u120.sk <- pp.cohort.1 %>%  filter(under120h == TRUE, sane_kit_YN == "Yes", female == 1, english == 1)
pp.primary.results.120.sk<-f.advocate.regression(pp.u120.sk, pp.u120.sk$exposure)
primary.results.120.sk<-f.advocate.regression(pathway.u120.sk, pathway.u120.sk$exposure)
table.reg.sk120 <- tbl_merge(list(pp.primary.results.120.sk, primary.results.120.sk), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate if SANE Kit Done")
table.reg.sk120
```
#### Terteriary Outcome: _Advocate Contacted/Offerred *IF* SANE Kit **Offered** (restricted to English speaking female patients)_

```{r}
pathway.u120.sk_o <- cohort.1 %>% filter(under120h == TRUE, sane_kit_offered == "Sane Kit Offered", female == 1, english == 1)
pp.u120.sk_o <- pp.cohort.1 %>%  filter(under120h == TRUE, sane_kit_offered == "Sane Kit Offered", female == 1, english == 1)
pp.primary.results.120.sk_o<-f.advocate.regression(pp.u120.sk_o, pp.u120.sk_o$exposure)
primary.results.120.sk_o<-f.advocate.regression(pathway.u120.sk_o, pathway.u120.sk_o$exposure)
table.reg.sk120_o <- tbl_merge(list(pp.primary.results.120.sk_o, primary.results.120.sk_o), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of documentation of offering call to PT advocate if SANE Kit Offerred")
table.reg.sk120_o
```

### Secondary Outcome: _For Women =/< 55 Presenting  < 120 Hours_

```{r}
preg.test.reg<-function(data, exposure){
  model<-glm(pregnancy_test_ordered_num ~ exposure + white + english + ambulance + age + intoxicated, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}

preg.prev.reg<-function(data, exposure){
   model<-glm(prevent.preg ~ exposure + white + english + ambulance + age + intoxicated, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```
Pregnancy test ordered?
```{r preg test reg table}
preg.test.pp<-pp.u120 %>% filter(female == 1, age <= 55) %>% preg.test.reg(., .$exposure)
preg.test.path<-pathway.u120 %>% filter(female == 1, age <= 55) %>% preg.test.reg(., .$exposure)
table.reg.pregtest <- tbl_merge(list(preg.test.pp, preg.test.path), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of Pregnancy Test Ordered (if =/<55 & <120 hrs)")
table.reg.pregtest

```
Pregnancy prophylaxis ordered?

```{r preg pep table}
preg.prev.pp<-pp.u120 %>% filter(female == 1, age <= 55) %>% preg.prev.reg(., .$exposure)
preg.prev.path<-pathway.u120 %>% filter(female == 1, age <= 55) %>% preg.prev.reg(., .$exposure)
table.reg.pregprev <- tbl_merge(list(preg.prev.pp, preg.prev.path), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of Pregnancy Prophylaxis Ordered (if =/<55 & <120 hrs)")
table.reg.pregprev
```
### Secondary Outcome: _HIV PEP_ 

```{r Hiv PEP fxn}
hiv.pep.reg<-function(data, exposure){
  model<-glm(hiv_pep_kit_ordered_num ~ exposure + white + english + ambulance + age + intoxicated, family = "binomial", data = data)
  model.results <- tbl_regression(model, exponentiate = TRUE) %>% add_global_p()
  return(model.results)
}
```

```{r HIV PEP table}
pathway.u72 <- cohort.1 %>% filter(u72 == 1)
pp.u27 <- pp.cohort.1 %>% filter(u72 == 1)

tbl.pep.pp <- hiv.pep.reg(pp.u27, pp.u120$exposure)
tbl.pep.path <- hiv.pep.reg(pathway.u72, pathway.u72$exposure)
tbl.pep.hiv <- tbl_merge(list(tbl.pep.pp, tbl.pep.path), tab_spanner = c("**Pre v. Post**", "**Pathway v. No Pathway**")) %>% as_gt() %>% tab_header("Odds of Receiving HIV PEP if Presented to ED <72 Hours Since Assault")
tbl.pep.hiv
```

## Graphs

### Percent pathway, sane kit done and advocate offered over time

```{r line over time graphs}
month_line_df <-
  pp.cohort.1 %>% mutate(
    month = floor_date(arrive_dt, unit = "month"),
    advocate = case_when(
      advocate_offered == "Advocate Offered" ~ 1,
      advocate_offered == "No Documentation of Pt Advocate" ~ 0,
      .default = NA
    ),
    did_SANE_kit = if_else(sane_kit_YN == "Yes", 1, 0)
  ) %>%
  group_by(month) %>% summarise(
    Percent_Advocate = mean(advocate)*100,
    Percent_Pathway = mean(agile_md_used_num)*100,
    Percent_Sane = mean(did_SANE_kit)*100
  ) %>% gather(key = "Metric", value = "Percent", -month)

month_line_df %>% ggplot(aes(x = month, y = Percent, color = Metric)) + geom_point() + geom_path() 

quarter_line_df <-
  pp.cohort.1 %>% mutate(
    quarter = ceiling_date(arrive_dt, unit = "quarter"),
    advocate = case_when(
      advocate_offered == "Advocate Offered" ~ 1,
      advocate_offered == "No Documentation of Pt Advocate" ~ 0,
      .default = NA
    ),
    did_SANE_kit = if_else(sane_kit_YN == "Yes", 1, 0)
  ) %>%
  group_by(quarter) %>% summarise(
    Percent_Advocate = mean(advocate),
    Percent_Pathway = mean(agile_md_used_num),
    Percent_Sane = mean(did_SANE_kit)
  ) %>% gather(key = "Metric", value = "Percent", -quarter) %>% filter(Percent !=0)

quarter_percent_plot<- quarter_line_df %>% ggplot(aes(x = quarter, y = Percent, color = Metric)) + geom_point() + geom_path() + theme_minimal() + scale_fill_brewer(palette = "Set1") + scale_y_continuous(labels = scales::percent) + ylim(0, 1) + geom_vline(xintercept = pathway_start, color = "black", linetype= 'longdash') + geom_vline(xintercept = sb_start, color= "darkgrey", linetype= 'longdash')
quarter_percent_plot
```



### Percent pathway utilization over time
```{r}
time_graph_1 <- all_pts %>% mutate(month = floor_date(arrive_dt, "month")) %>% ggplot() + geom_bar(mapping = aes(x = month, fill = pathway)) + theme_minimal() + scale_fill_brewer(palette = "Set1")
time_graph_1

ppm <- all_pts %>% mutate(month = floor_date(arrive_dt, "month")) %>% group_by(month) %>% summarise(n = n(), pathway = sum(agile_md_used_num), percent.path = 100*(sum(agile_md_used_num)/n())) %>% mutate(no_pathway = n - pathway) %>% select(-n) %>%  gather(key = "visit_type", value = "visits", -month, -percent.path)
ppm %>% ggplot() + geom_col(aes(x = month, y = visits, fill = visit_type)) + geom_borderline(aes(x = month, y = percent.path), color = "#377EB8", bordercolour = "grey", borderwidth = 0.25) + labs(title = "Patients per month", y = "Number of visits", x= "Month", fill = "Pathway") + theme_minimal() + scale_fill_brewer(palette = "Set1") + scale_y_continuous(sec.axis=sec_axis(~.*0.01, name="Percent of Visits with Pathway Used", labels=scales::percent))
ppq <- all_pts %>% mutate(quarter = floor_date(arrive_dt, "quarter")) %>% group_by(quarter) %>% summarise(n = n(), pathway = sum(agile_md_used_num), percent.path = 100*(sum(agile_md_used_num)/n())) %>% mutate(no_pathway = n - pathway) %>% select(-n) %>%  gather(key = "visit_type", value = "visits", -quarter, -percent.path)
ppq %>% ggplot() + geom_col(aes(x = quarter, y = visits, fill = visit_type)) + geom_borderline(aes(x = quarter, y = percent.path), color = "#377EB8", bordercolour = "grey", borderwidth = 0.25) + labs(title = "Patients per quarter", y = "Number of visits", x= "quarter", fill = "Pathway") + theme_minimal() + scale_fill_brewer(palette = "Set1") + scale_y_continuous(sec.axis=sec_axis(~.*0.01, name="Percent of Visits with Pathway Used", labels=scales::percent))
```

### OR Graph
```{r}
OR_Data<- read_excel("~/Documents/Current_Projects/Sexual_Assault/new_SA_YNHH/Updated YNHH SA code/OR_Table_Data.xlsx") %>% mutate(lnOR = log(OR), lnLCI = log(LCI), lnUCI=log(UCI))
CI_Plot <- ggplot(OR_Data, aes(x = factor(Exposure), y = OR, color = factor(Exposure))) + geom_errorbar(aes(ymin =`LCI`, ymax = `UCI`), position = "dodge") + facet_wrap(vars(Measure)) + geom_hline (yintercept = 1, linetype = "dashed")
CI_Plot + theme_light() + guides(color = F)
lnCI_Plot <- ggplot(OR_Data, aes(x = factor(Exposure), y = lnOR, color = factor(Exposure))) + geom_errorbar(aes(ymin =`lnLCI`, ymax = `lnUCI`), position = "dodge") + facet_wrap(vars(Measure), labeller = labeller(Measure = label_wrap_gen(50))) + geom_hline (yintercept = 0, linetype = "dashed")
lnCI_Plot + guides(color = F) + theme_light() + theme(axis.text.x = element_text(angle = 90), axis.title.x = element_blank()) 

```
## Supplement
```{r excluded patients}
all_excluded<-all_pts %>% filter(age > 18) %>% filter(!is.na(exclude) | sane_kit_done == 4 | between == 1) %>% mutate(reason_to_exclude = case_when(
  between == 1 ~ 7,
  is.na(reason_to_exclude) ~ 6,
  .default = reason_to_exclude)) %>% add_value_labels(reason_to_exclude = c( "Seen earlier" = 1 , "Patient reports not being assaulted" = 2, "Psych" = 3, "not excluded" = 4, "Eloped" = 5, "NA/Not Listed" = 6, "Between Period" = 7)) %>% to_factor()

excluded_plot <- excluded_patients %>% filter(between == 0) %>%  ggplot(aes(x = reason_to_exclude)) + geom_bar(fill = "darkred") + geom_text(stat='count', aes(label=..count..), vjust=-1) + theme_minimal()
all_excluded

```

